---
title: "binary_model_admin1"
author: "Qianyu Dong"
date: "2023-02-22"
output: html_document
---


```{r, echo=FALSE,message=FALSE, warning= FALSE}
library(dplyr)
library(rgdal)
options(warn=0)
library(spdep)
library(SUMMER)
library(geosphere)
library(stringr)
library(tidyverse)
#devtools::install_github("ropensci/rdhs")
library(rdhs)
library(Hmisc)
library(labelled)
library(INLA)
# libraries needed
# library(tidyverse)  # most variable creation here uses tidyverse 
# library(tidyselect) # used to select variables in FP_EVENTS.R
# library(haven)      # used for Haven labeled DHS variables
# library(labelled)   # used for Haven labeled variable creation
# library(expss)    # for creating tables with Haven labeled data
# library(xlsx)     # for exporting to excel
library(naniar)   # to use replace_with_na function
library(here)       # to get R project path
library(patchwork) # organize ggplot2 output nicely
```


```{r}
# setwd(here())
children <- readRDS(here("data/DHS_data/ZMKR71DT.rds"))
births <- readRDS(here("data/DHS_data/ZMBR71DT.rds"))
individual <- readRDS(here("data/DHS_data/ZMIR71DT.rds"))
household <- readRDS(here("data/DHS_data/ZMHR71DT.rds"))
```



```{r,RH_ANC.R }

IRdata <- individual %>%
  mutate(wt = v005/1000000)

# period and age of child
# choose reference period, last 2 years (24 months) or last 5 years (60 months)
# Using a period of the last 2 years will not match final report but would provide more recent information.
# period = 24
IRdata <- IRdata %>%
  mutate(period = 60)

# age of child. If b19_01 is not available in the data use v008 - b3_01
if ("TRUE" %in% (!("b19_01" %in% names(IRdata))))
  IRdata [[paste("b19_01")]] <- NA
if ("TRUE" %in% all(is.na(IRdata $b19_01)))
{ b19_included <- 0} else { b19_included <- 1}

if (b19_included==1) {
  IRdata <- IRdata %>%
    mutate(age = b19_01)
} else {
  IRdata <- IRdata %>%
    mutate(age = v008 - b3_01)
}


# //Number of ANC visits in 4 categories that match the table in the final report
IRdata <- IRdata %>%
  mutate(rh_anc_numvs =
           case_when(
             m14_1 == 0 ~ 0 ,
             m14_1 == 1 ~ 1 ,
             m14_1  %in% c(2,3)   ~ 2 ,
             m14_1>=4 & m14_1<=90  ~ 3 ,
             m14_1>90  ~ 9 ,
             age>=period ~ 99 )) %>%
  replace_with_na(replace = list(rh_anc_numvs = c(99))) %>%
  set_value_labels(rh_anc_numvs = c(none = 0, "1" = 1, "2-3"=2, "4+"=3, "don't know/missing"=9  )) %>%
  set_variable_labels(rh_anc_numvs = "Number of ANC visits")

# //4+ ANC visits  
IRdata <- IRdata %>%
  mutate(rh_anc_4vs =
           case_when(
             rh_anc_numvs==3 ~ 1,
             rh_anc_numvs %in% c(0,1,2,9)   ~ 0 )) %>%
  set_value_labels(rh_anc_4vs = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(rh_anc_4vs = "Attended 4+ ANC visits")


```

Comment: the following reproduces the same as DHS code it seems? Then we should use the DHS codes and then modify `IRdata` object accordingly below (so that for future adaptation to other indicators we could just replace the top chunk.)

```{r}
raw.dat.tmp<-IRdata
  strat <- attr(raw.dat.tmp$v025,which='labels')
  names(strat) <- tolower(names(strat))
  raw.dat.tmp$v025 <- ifelse(raw.dat.tmp$v025 == strat["urban"][[1]],'urban','rural')
  raw.dat.tmp$v025 <- factor(raw.dat.tmp$v025, levels = c('urban','rural'))
  raw.dat.tmp$v024 <- factor(unlabelled(raw.dat.tmp$v024))
  
#using rh_anc_4vs from dhs code
  #  dat.tmp<-  raw.dat.tmp %>%
  # dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
  #            Antenatal="rh_anc_4vs")) %>%
  #      replace(is.na(.), 0)

   

   dat.tmp<-  raw.dat.tmp %>%
    # filter( b19_01<=60)%>%#for indiviudal file
     #filter( b19<=60)%>% #for birth file
  dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
             Antenatal="rh_anc_4vs")) %>% # Antenatal="m14" for birth file
    # mutate(Antenatal = ifelse(Antenatal>3 &  Antenatal<98,1,0)) %>%
    # replace(is.na(.), 0)
    drop_na()


 # hist(dat.tmp$Antenatal,main = "Numbers of Antenatal visits>4 in each cluster")
 
  
```

```{r}
table(dat.tmp$Antenatal)
```


```{r}
weight.strata.adm1.u1 <- readRDS(here("data/UR/U1_fraction/admin1_u1_urban_weights.rds"))
weight.strata.adm1.u1_2018<-subset(weight.strata.adm1.u1, years == 2018)
```


```{r}
poly.adm1<-readRDS(here("data/Geo/poly.adm1.rds"))
admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
```


# admin-1 plots

Comment: The region name matching needs to be handled in a more systematic way. But here I created the lookup table interactively
```{r}
admin1_name_table <- data.frame(by.data = sort(unique(dat.tmp$region)), by.geo = sort(poly.adm1$NAME_1))
admin1_name_table[7, 2] <- "Northern"
admin1_name_table[8, 2] <- "North-Western"
admin1_name_table$sID <- match(admin1_name_table[, 2], poly.adm1$NAME_1)
```


```{r , fig.show="hold", out.width="100%"}

par(mar = c(4, 4, .1, .1))

dat.tmp.tem <- dat.tmp %>%
      group_by(region) %>%
      summarise(Total = sum(Antenatal > -1, na.rm = t), 
                Antenatal = sum(Antenatal, na.rm = t),) %>%
      mutate(Prop = Antenatal / Total) %>% as.data.frame()

dat.tmp.tem$region <- admin1_name_table[match(dat.tmp.tem$region, admin1_name_table[,1]), 2]
   
g1 <- mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Count")
g2 <- mapPlot(dat.tmp.tem,
          variables = "Total",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Total")
g3 <- mapPlot(dat.tmp.tem,
          variables = "Prop",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Prop (unweighted)")
g1 + g2 + g3    

```



# Admin-1 direct and smoothed direct estimators

#### Direct estimates

For $y_j$ be the $j_th$ individual result and $w_j$ denote the design weight associated with this individual. Let i be area i.model

$$ \hat p^{HT}_{i}=\frac {\sum_{j \in i} y_j w_j}{\sum_{j \in i} w_j}$$

#### Smoothed direct estimates


Use direct estimate $\hat p^{HT}_{i}$ to estimate the true prevalence with random effects model,
$$log(\hat p^{HT}_{i})|\lambda_{i} \sim\textrm{Normal}(\lambda_{i}, V_{i}^{HT}),$$
$$\lambda_{i}= \mathbf x_i^{T} \mathbf{\beta} +S_i+e_i.$$
$x_i$ are areal-level covariates, $S_i$ are structured spatial trends that follow BYM model, and $e_i$ are unstructured spatial errors. Expit($p_{i}$) is the true prevalence.



Comment: in `smoothSurvey()`, the strata variable is the actual survey stratification variable, which is usually Admin1 crossed with U/R, instead of only the within-area stratification variable (U/R only).

Comment: I make the names consistent in both the data and the polygon files to avoid changing the labels multiple times later.

```{r}
   bino.dat.tmp<-dat.tmp
   bino.dat.tmp$strata.full <- paste(bino.dat.tmp$region, bino.dat.tmp$strata)
   bino.dat.tmp$region <- admin1_name_table[match(bino.dat.tmp$region, admin1_name_table[,1]), 2]

   admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
   admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
   colnames(admin1.mat) <- rownames(admin1.mat) <-  poly.adm1$NAME_1
   
   fit1 <- smoothSurvey(as.data.frame(bino.dat.tmp),
            responseType =  "binary",
            responseVar= "Antenatal",
            regionVar = "region",
            clusterVar = "~cluster+householdID",#+householdID same result
            weightVar = "weight",
            strataVar = "strata.full",
            Amat =admin1.mat,
            CI = 0.95)  
```

```{r}
  fit1$HT
```

```{r}
  fit1$smooth
```

```{r}
fit1$HT$HT.sd <- sqrt(fit1$HT$HT.var)
fit1$smooth$sd <- sqrt(fit1$smooth$var)
ylim1 <- range(c(fit1$HT$HT.est, fit1$smooth$mean))
ylim2 <- range(c(fit1$HT$HT.sd, fit1$smooth$sd))
```

```{r HT, fig.show="hold", out.width="100%"}
g1 <- mapPlot(fit1$HT,
          variables = "HT.est",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "HT estimator", 
          ylim = ylim1)
g2 <- mapPlot(fit1$HT,
          variables = "HT.sd",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "HT SE", 
          ylim = ylim2)

g3 <- mapPlot(fit1$smooth,
          variables = "mean",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "Smooth Direct estimator", 
          ylim = ylim1)

g4 <- mapPlot(fit1$smooth,
          variables = "sd",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "Smooth Direct SE", 
          ylim = ylim2)
(g1 + g2)/(g3 + g4)
```





# admin-1 Beta-Binomial model with IID space effect

#### cluster model
$Y_c$ is the number of events in cluster c, and $n_c$ denote the number of individuals at risk c= 1,$\dots$,C.

$$Y_c|p_c,d\sim \textrm{Beta Binomial}(n_c,p_c,d),$$
$$p_c=\textrm{expit}(\alpha+x_c\beta+e_{i[s_c]}+S_{i[s_c]}),$$
where $\alpha$ is the intercept, $x_c$ are cluster-specific covariates, $e_i\overset{\text{iid}}\sim N(0,\sigma_e^2),[s_1,\dots,s_n]\sim ICAR(\sigma^2_c,\phi),$ $i[s_c]$ denotes “the area i within which the cluster $s_c$resides. Areal-level risk: $p_i=expit(\alpha+x_c\beta+e_{i}+S_{i})$


Comment: `c.dat.tmp.birth` object name is probably too long and not clear what it is...

```{r}

   c.dat.tmp <- dat.tmp %>%
    group_by(cluster) %>%
    mutate(n = length(cluster)) %>%
    mutate(Antenatal = sum(Antenatal,na.rm = T)) %>%
    ungroup()%>%
    distinct( cluster, .keep_all = TRUE)
```


Comment: I matched on the lookup table to make sure sID correspond to the same order as in the adjacency matrix.

Comment: updated prior to be PC prior.

```{r}
nregion <- dim(admin1_name_table)[1]
# add new rows corresponding to each region
c.dat.tmp[(dim(c.dat.tmp)[1]+1):(dim(c.dat.tmp)[1]+nregion),"region"] <- admin1_name_table[,1]

c.dat.tmp$ID <- 1:dim(c.dat.tmp)[1]
c.dat.tmp$sID <- admin1_name_table$sID[match(c.dat.tmp$region, admin1_name_table[,1])]

pc.u = 1
pc.alpha = 0.01
formula <- Antenatal ~ 1 + f(sID, model = "iid", hyper = list(prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha))))
imod_0 <- inla(formula, 
               family="betabinomial",
               data=c.dat.tmp,
               Ntrials=n,
               control.predictor = list(compute=TRUE, link = 1))
tail(imod_0$summary.fitted.values,n=nregion)

```


```{r iid, fig.show="hold", out.width="50%"}
dat.tmp.tem <- as.data.frame(cbind(
  region=poly.adm1$NAME_1[tail(c.dat.tmp$sID,n=nregion)],
  Antenatal= tail(imod_0$summary.fitted.values,n=nregion)[,1]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1", 
          legend.label = "BB (iid)")
  
  
dat.tmp.tem<- as.data.frame(cbind(
        region=poly.adm1$NAME_1[tail(c.dat.tmp$sID,n=nregion)],
        Antenatal= tail(imod_0$summary.fitted.values,n=nregion)[,2]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",
          legend.label = "SD BB (iid)")
  
```




# Admin-1 Beta-Binomial model with BYM2 spatial effect


Comment: I use the same dataset as before to avoid copy pasting errors.

```{r}
formula <- Antenatal ~ 1+ f(sID, model = "bym2", graph = admin1.mat, scale.model = TRUE, hyper = list(prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha))))
imod_1 <- inla(formula, 
               family="betabinomial",
               data=c.dat.tmp,
               Ntrials=n,
               control.predictor = list(compute=TRUE, link = 1))
```


```{r bym, fig.show="hold", out.width="50%"}
dat.tmp.tem<- as.data.frame(cbind(
                  region=poly.adm1$NAME_1[tail(c.dat.tmp$sID,n=nregion)],
                  Antenatal= tail(imod_1$summary.fitted.values,n=nregion)[,1]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1", 
          legend.label = "BB (BYM2)")
  
  
dat.tmp.tem<- as.data.frame(cbind(
        region=poly.adm1$NAME_1[tail(c.dat.tmp$sID,n=nregion)],
        Antenatal= tail(imod_1$summary.fitted.values,n=nregion)[,2]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",
          legend.label = "SD BB (BYM2)")
```



# admin-1 model with strata


$$Y_c|p_c,d\sim \textrm{Beta Binomial}(n_c,p_c,d)$$


$$p_c=\textrm{expit}(\alpha+\gamma\times I(s_c \in \textrm{urban})+x_c\beta+e_{i[s_c]}+S_{i[s_c]})$$
Area-level risk: $p_i=q_i\times expit(\alpha+x_c\beta+e_{i}+S_{i})+(1-q_i)\times expit(\alpha+x_c\beta+e_{i}+S_{i})$, where $q_i$ is the proportion of the relevant population in area i.


Comment: I also removed repeated data generating steps and built from previous data frame.

```{r, out.width="50%"}

c.dat.tmp[(dim(c.dat.tmp)[1]-nregion+1):(dim(c.dat.tmp)[1]),"strata"]<-  "urban"
tmp <- c.dat.tmp[(dim(c.dat.tmp)[1]-nregion+1):(dim(c.dat.tmp)[1]), ]
tmp$strata <- "rural"
c.dat.tmp <- rbind(c.dat.tmp, tmp)

pc.u.phi <- 0.5 
pc.alpha.phi <- 2/3 

formula <- Antenatal ~ 1 + strata + 
            f(sID, model = "bym2", graph = admin1.mat, 
              hyper = list(
                  prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha)), 
                  phi = list(prior = 'pc', param = c(pc.u.phi , pc.alpha.phi))))

imod_1_strata <- inla(formula, 
                    family="betabinomial",
                    data=c.dat.tmp,
                    Ntrials=n,
                    control.predictor = list(compute=TRUE, link = 1), 
                    control.compute = list(config = TRUE))

summary(imod_1_strata)
    
```

Urban/rural specific estimates from INLA linear combinations

```{r, out.width="100%"}
dat.tmp.tem<- data.frame( 
                  region=rep(poly.adm1$NAME_1[tail(c.dat.tmp$sID,n=nregion)], 2),
                  Antenatal=  tail(imod_1_strata$summary.fitted.values[, 1],n = 2 * nregion), 
                  strata = tail(c.dat.tmp$strata, n = 2 * nregion))
mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "strata",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",
          is.long = TRUE, 
          legend.label = "BB stratified") 
  
```

Combined results using posterior draws. 

Comment: need to check the row index in weight matrix is the same as the adjacency matrix (i.e., sID variable). Also may need to add an if-statement to account for strata variable baseline value being either urban or rural (for future pipeline).

```{r, out.width="100%"}
nsamp <- 1000
samp <- inla.posterior.sample(n = nsamp, result = imod_1_strata, intern = TRUE)

draw.u <- matrix(NA, nsamp, nregion)
draw.r <- matrix(NA, nsamp, nregion)
draw.all <- matrix(NA, nsamp, nregion)
for(i in 1:length(samp)){
  tmp <- samp[[i]]$latent
  s.effect <- tmp[paste0("sID:", 1:nregion), 1]
  intercept <- tmp["(Intercept):1", 1]
  str.effect <- tmp["stratarural:1", 1]
  draw.u[i, ] <- s.effect + intercept
  draw.r[i, ] <- s.effect + intercept + str.effect
  draw.all[i, ] <- expit(draw.u[i, ]) * weight.strata.adm1.u1_2018$urban + 
                   expit(draw.r[i, ]) * (1 - weight.strata.adm1.u1_2018$urban)
}

post.u <- apply(draw.u, 2, mean)
post.r <- apply(draw.r, 2, mean)
post.all <- apply(draw.all, 2, mean)

dat.tmp.tem <- data.frame(mean = c(post.u, post.r, post.all), 
                          type = c(rep("urban", nregion), rep("rural", nregion), 
                            rep("aggregated", nregion)))
dat.tmp.tem$region <- rep(poly.adm1$NAME_1, 3)

mapPlot(dat.tmp.tem,
          values = "mean",
          variables= "type",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = TRUE, 
          legend.label = "BB stratified")
  
```


Comment: maybe here also make a plot of urban proportion, just for exploratory purpose.

```{r urban proportion}

dat.tmp.tem<- data.frame(
        region=poly.adm1$NAME_1,
        urban_prop= c(weight.strata.adm1.u1_2018$urban ))

mapPlot(dat.tmp.tem,
          variables = "urban_prop",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",
          legend.label = "urban proportion")
```

```{r}
tb<-data.frame(region=fit1$HT$region, 
               est.HT=fit1$HT$HT.est,sd.HT=sqrt(fit1$HT$HT.var),
               est.smth=fit1$smooth$mean,sd.smth=sqrt(fit1$smooth$var),
               est.bb.strat=apply(draw.all, 2, mean),sd.bb.strat=apply(draw.all, 2, sd),
                 est.bb.bym= tail(imod_1$summary.fitted.values,n=nregion)[,1],
                sd.bb.bym=tail(imod_1$summary.fitted.values,n=nregion)[,2],
                 est.bb.iid= tail(imod_0$summary.fitted.values,n=nregion)[,1],
                sd.bb.iid=tail(imod_0$summary.fitted.values,n=nregion)[,2]
               
               
               )

 # write.csv(tb, "zambia.anc.admin1.csv")


tb %>%
  pivot_longer(  cols = starts_with("est"),
                 names_to = c("est"))%>%
  ggplot(data=., aes(x=region, y=value, group=est)) +
  geom_line(aes(col=est))


tb %>%
  pivot_longer(  cols = starts_with("sd"),
                 names_to = c("sd"))%>%
  ggplot(data=., aes(x=region, y=value, group=sd)) +
  geom_line(aes(col=sd))
```


