---
title: "binary_comparison"
# author: "Qianyu Dong"
# date: "2023-04-20"
output: html_document
---



```{r, echo=FALSE,message=FALSE, warning= FALSE}
library(dplyr)
library(rgdal)
options(warn=0)
library(spdep)
library(SUMMER)
library(geosphere)
library(stringr)
library(tidyverse)
#devtools::install_github("ropensci/rdhs")
library(rdhs)
library(Hmisc)
library(labelled)
library(INLA)
# libraries needed
# library(tidyverse)  # most variable creation here uses tidyverse 
# library(tidyselect) # used to select variables in FP_EVENTS.R
# library(haven)      # used for Haven labeled DHS variables
# library(labelled)   # used for Haven labeled variable creation
# library(expss)    # for creating tables with Haven labeled data
# library(xlsx)     # for exporting to excel
library(naniar)   # to use replace_with_na function
library(here)       # to get R project path
library(patchwork) # organize ggplot2 output nicely
```


### Ratio comparison

```{r,  echo=FALSE}
load(file = "/Users/qianyu/Dropbox/binary_model/Results/Zambia/ModelResult/ratio.rda")
```


```{r,  echo=FALSE}

df<-data.frame(pop_r=pop$pop_r,survey_weight_r=survey_weight$survey_weight_r)
ggplot(df, aes(survey_weight_r,pop_r)) +
  geom_point(alpha = 0.5,size =pop$admin2_pop/50000)+
    geom_abline(slope = 1, intercept = 0, linetype = "dashed")+
    labs(title = "admin 2 survey weight ratio & 15-49 female population ratio")

```

Point size by admin2 population size. 





### Scatter plot, results vs admin 1 direct estimate 

```{r, echo=FALSE,out.width="50%",fig.width = 4, fig.height = 4}
load(file = "/Users/qianyu/Dropbox/binary_model/Results/Zambia/ModelResult/admin1.rda")
#admin1_dir, admin1_bbm_strata
load(file = "/Users/qianyu/Dropbox/binary_model/Results/Zambia/ModelResult/admin2.rda")
##dmin2_strata_agg,admin2_strata,dat.tmp.tem_HT_admin1,HT

```



###### admin 1 smoothed vs admin 1 direct estimate 


```{r,echo=FALSE,out.width="50%",fig.width = 4, fig.height = 4}

plot(admin1_dir$HT$HT.est,admin1_dir$smooth$mean,
     xlim=round(range(admin1_dir$HT$HT.est,admin1_dir$smooth$mean),digits = 4),
     ylim=round(range(admin1_dir$HT$HT.est,admin1_dir$smooth$mean),digits = 4),
     xlab = "admin1 Direct", ylab = "admin1 Smoothed Direct", main = "estimation")
abline(a = 0, b = 1, col = "red")


plot((admin1_dir$HT$HT.sd),admin1_bbm_strata$sd[21:30],
     xlab = "admin1 Direct", ylab = "admin1 Smoothed Direct", main = "SD",
     xlim=round(range(admin1_dir$HT$HT.sd,admin1_dir$smooth$sd),digits = 4),
     ylim=round(range(admin1_dir$HT$HT.sd,admin1_dir$smooth$sd),digits = 4)
     )
abline(a = 0, b = 1, col = "red")
```





##### admin1_bbm_strata vs admin 1 direct estimate 


```{r, echo=FALSE, out.width="50%",fig.width = 4, fig.height = 4}

plot(admin1_dir$HT$HT.est,admin1_bbm_strata$mean[21:30],
     xlim=round(range(admin1_dir$HT$HT.est,admin1_bbm_strata$mean[21:30]),digits = 4),
     ylim=round(range(admin1_dir$HT$HT.est,admin1_bbm_strata$mean[21:30]),digits = 4),
     xlab = "admin1 Direct", ylab = "admin1 bbm strata", main = "estimation")
abline(a = 0, b = 1, col = "red")


plot((admin1_dir$HT$HT.sd),admin1_bbm_strata$sd[21:30],
     xlab = "admin1 Direct", ylab = "admin1 bbm strata", main = "SD",
     xlim=round(range(admin1_dir$HT$HT.sd,admin1_bbm_strata$sd[21:30]),digits = 4),
     ylim=round(range(admin1_dir$HT$HT.sd,admin1_bbm_strata$sd[21:30]),digits = 4)
     )
abline(a = 0, b = 1, col = "red")
```


##### admin2 direct vs admin 1 direct estimate 



```{r, echo=FALSE, out.width="50%",fig.width = 4, fig.height = 4}

plot(admin1_dir$HT$HT.est,dat.tmp.tem_HT_admin1$Antenatal,
     xlim=round(range(admin1_dir$HT$HT.est,dat.tmp.tem_HT_admin1$Antenatal),digits = 4),
     ylim=round(range(admin1_dir$HT$HT.est,dat.tmp.tem_HT_admin1$Antenatal),digits = 4),
     xlab = "admin1 Direct", ylab = "admin2 Direct", main = "estimation(by pop)")
abline(a = 0, b = 1, col = "red")

#
plot(admin1_dir$HT$HT.est,dat.tmp.tem_HT_admin1_sw$Antenatal,
     xlim=round(range(admin1_dir$HT$HT.est,dat.tmp.tem_HT_admin1_sw$Antenatal),digits = 4),
     ylim=round(range(admin1_dir$HT$HT.est,dat.tmp.tem_HT_admin1_sw$Antenatal),digits = 4),
     xlab = "admin1 Direct", ylab = "admin2 Direct", main = "estimation(by survey weight)")
abline(a = 0, b = 1, col = "red")


```



##### admin2_bbm_strata vs admin 1 direct estimate 


```{r, echo=FALSE,out.width="50%",fig.width = 4, fig.height = 4}
library(matrixStats)

 admin2_stra_tem<-  admin2_strata_agg[admin2_strata_agg$type==c("aggregated"),"mean"]
plot(admin1_dir$HT$HT.est,admin2_stra_tem,
     xlim=round(range(admin1_dir$HT$HT.est,admin2_stra_tem),digits = 4),
     ylim=round(range(admin1_dir$HT$HT.est,admin2_stra_tem),digits = 4),
     xlab = "admin1 Direct", ylab = "admin2 bbm strata", main = "estimation")
abline(a = 0, b = 1, col = "red")


 admin2_stra_tem<-  admin2_strata_agg[admin2_strata_agg$type==c("aggregated"),"sd"]
plot(admin1_dir$HT$HT.sd,admin2_stra_tem,
     xlim=round(range(admin1_dir$HT$HT.sd,admin2_stra_tem),digits = 4),
     ylim=round(range(admin1_dir$HT$HT.sd,admin2_stra_tem),digits = 4),
     xlab = "admin1 Direct", ylab = "admin2 bbm strata", main = "sd")
abline(a = 0, b = 1, col = "red")

```








##### admin2_bbm_strata vs admin 2 direct estimate 



```{r, echo=FALSE, warning==FALSE,out.width="50%",fig.width = 4, fig.height = 4}
library(matrixStats)

admin2_strata_tem<-admin2_strata[admin2_strata$type==c("aggregated"),"mean"]
plot(HT$response0,admin2_strata_tem,
     xlim=round(range(HT$response0,admin2_strata_tem,na.rm = T),digits = 4),
     ylim=round(range(HT$response0,admin2_strata_tem,na.rm = T),digits = 4),
     xlab = "admin 2 Direct", ylab = "admin2 bbm strata", main = "estimation")
abline(a = 0, b = 1, col = "red")



```





### Line charts 





```{r, echo=FALSE,fig.show="hold", out.width="50%"}

fit1<-admin1_dir

tb<-data.frame(region=fit1$HT$region, 
               est.HT=fit1$HT$HT.est,
               sd.HT=sqrt(fit1$HT$HT.var),
               est.smth=fit1$smooth$mean,
               sd.smth=sqrt(fit1$smooth$var),
               # lower.smth=fit1$smooth$lower,
               # upper.smth=fit1$smooth$upper,
               est.bb.strat=admin1_bbm_strata$mean[21:30],
               sd.bb.strat=admin1_bbm_strata$sd[21:30],
               # lower.strat=admin1_bbm_strata$lbd[21:30],
               # upper.strat=admin1_bbm_strata$ubd[21:30]
               
               est.HT.admin2=dat.tmp.tem_HT_admin1$Antenatal,
               est.bb.strat.admin2=admin2_strata_agg$mean[21:30],
               sd.bb.strat.admin2=admin2_strata_agg$sd[21:30]
               
               
               )

  # write.csv(tb, "zambia.anc.admin1.csv")


tb %>%
  pivot_longer(  cols = starts_with("est"),
                 names_to = c("est"))%>%
  ggplot(data=., aes(x=region, y=value, group=est)) +
  geom_line(aes(col=est))


tb %>%
  pivot_longer(  cols = starts_with("sd"),
                 names_to = c("sd"))%>%
  ggplot(data=., aes(x=region, y=value, group=sd)) +
  geom_line(aes(col=sd))

```










### Intervals


```{r,warning=FALSE,echo=FALSE,fig.show="hold", out.width="50%"}

# dt<-admin2_strata[admin2_strata$type==""]
plot_fun <- function(dat) {
  ggplot(dat, aes(x = NAME_2, y = mean)) +
    geom_point() +
    geom_errorbar(aes(ymin = ubd , ymax = lbd,color = type), alpha = 0.2) +
      scale_color_manual(values = c("red", "blue", "green"))+

    geom_hline(yintercept = as.numeric(admin1_dir$HT[admin1_dir$HT$region == unique(dat$NAME_1), "HT.est"]),
               linetype = "dashed",color="red") +
    geom_hline(yintercept = as.numeric(admin2_strata_agg[admin2_strata_agg$NAME_1 == unique(dat$NAME_1)&admin2_strata_agg$type==c("aggregated"), "mean"]),
               linetype = "dashed",color="blue") +
    labs(title = unique(dat$NAME_1))
  # scale_color_manual(values = c("red", "blue"), 
  #                    name = "Line Color", 
  #                    labels = c("Line 1", "Line 2"),
  #                    guide = guide_legend(override.aes = list(linetype = c("dashed", "dashed")))) +
  # theme(legend.position = "bottom")
}

# Loop over unique values of admin1.names
plots <- lapply(unique(admin2_strata$NAME_1), function(x) {
  dat <- admin2_strata %>% filter(NAME_1 == x)
  plot_fun(dat)
})

plots


```

Blue lines are admin2 strata model results and red lines are admin1 direct estimates.





### natinal

```{r}
country<-"Zambia"
home.dir<-"/Users/qianyu/Dropbox/binary_model"
data.dir <- paste0(home.dir,'/data/',country) # set the directory to store the data
res.dir <- paste0(home.dir,'/Results/',country) # set the directory to store the results (e.g. fitted R objects, figures, tables in .csv etc.)
info.name <- paste0(country, "_general_info.Rdata")
load(file = paste0(home.dir,'/data/Info/',info.name, sep='')) # load the country info
# admin2_pop<-readRDS(file=paste0(res.dir,'/UR/Uf_fraction/admin2_uf_2018_urban_frac.rds'))
admin1_pop<-readRDS(file=paste0(res.dir,'/UR/Uf_fraction/admin1_uf_2018_urban_frac.rds'))
nat_pop<-readRDS(file=paste0(res.dir,'/UR/Uf_fraction/natl_uf_urban_pop.rds'))

```

```{r}
# 
# admin1_wei<-readRDS(file=paste0(res.dir,'/UR/Uf_fraction/admin1_uf_urban_weights.rds'))
# admin1_wei
```


```{r}
# nat_pop
# sum(admin1_pop$total.c)
# admin1_pop
```

```{r}
dat.tmp.tem<-left_join(data.frame(NAME_1=admin1_pop$adm_name,pop=admin1_pop$total.c),
        data.frame(NAME_1=admin1_dir$HT$region,est=admin1_dir$HT$HT.est),by="NAME_1")
national.agg_admin1_direct<-  sum(dat.tmp.tem$pop/sum(dat.tmp.tem$pop)*dat.tmp.tem$est)
national.agg_admin1_direct 
```


```{r}
dat.tmp.tem<-left_join(data.frame(NAME_1=admin1_pop$adm_name,pop=admin1_pop$total.c),
        data.frame(NAME_1=admin1_dir$HT$region,est=tb$est.smth),by="NAME_1")
national.agg_admin1_smt.dir<-  sum(dat.tmp.tem$pop/sum(dat.tmp.tem$pop)*dat.tmp.tem$est)
national.agg_admin1_smt.dir 
```


```{r}
dat.tmp.tem<-left_join(data.frame(NAME_1=admin1_pop$adm_name,pop=admin1_pop$total.c),
        data.frame(NAME_1=admin1_dir$HT$region,est=tb$est.bb.strat),by="NAME_1")
national.agg_admin1_bb.strat<-  sum(dat.tmp.tem$pop/sum(dat.tmp.tem$pop)*dat.tmp.tem$est)
national.agg_admin1_bb.strat
```



```{r}

dat.tmp.tem<-left_join(data.frame(NAME_1=admin1_pop$adm_name,pop=admin1_pop$total.c),
        data.frame(NAME_1=admin1_dir$HT$region,est=tb$est.HT.admin2),by="NAME_1")
national.agg_admin2_direct<-  sum(dat.tmp.tem$pop/sum(dat.tmp.tem$pop)*dat.tmp.tem$est)
national.agg_admin2_direct
```


```{r}

dat.tmp.tem<-left_join(data.frame(NAME_1=admin1_pop$adm_name,pop=admin1_pop$total.c),
        data.frame(NAME_1=admin1_dir$HT$region,est=tb$est.bb.strat.admin2),by="NAME_1")
national.agg_admin2_bb.strat<-  sum(dat.tmp.tem$pop/sum(dat.tmp.tem$pop)*dat.tmp.tem$est)
national.agg_admin2_bb.strat
```


