---
title: "binary_admin_2"
author: "Qianyu Dong"
date: "2023-02-22"
output: html_document
---

```{r, echo=FALSE,message=FALSE, warning= FALSE}
library(dplyr)
library(rgdal)
options(warn=0)
library(spdep)
library(SUMMER)
library(geosphere)
library(stringr)
library(tidyverse)
#devtools::install_github("ropensci/rdhs")
library(rdhs)
library(Hmisc)
library(labelled)
library(INLA)
# libraries needed
# library(tidyverse)  # most variable creation here uses tidyverse 
# library(tidyselect) # used to select variables in FP_EVENTS.R
# library(haven)      # used for Haven labeled DHS variables
# library(labelled)   # used for Haven labeled variable creation
# library(expss)    # for creating tables with Haven labeled data
# library(xlsx)     # for exporting to excel
library(naniar)   # to use replace_with_na function
library(here)       # to get R project path
library(patchwork) # organize ggplot2 output nicely
```





```{r}
individual <- readRDS(here("data/DHS_data/ZMIR71DT.rds"))


country<-"Zambia"
home.dir<-"/Users/qianyu/Dropbox/binary_model"
data.dir <- paste0(home.dir,'/data/',country) # set the directory to store the data
# res.dir <- paste0(home.dir,'/Results/',country) # set the directory to store the results (e.g. fitted R objects, figures, tables in .csv etc.)
info.name <- paste0(country, "_general_info.Rdata")
load(file = paste0(home.dir,'/data/Info/',info.name, sep='')) # load the country info


```


```{r,RH_ANC.R }

IRdata <- individual %>%
  mutate(wt = v005/1000000)

# period and age of child
# choose reference period, last 2 years (24 months) or last 5 years (60 months)
# Using a period of the last 2 years will not match final report but would provide more recent information.
# period = 24
IRdata <- IRdata %>%
  mutate(period = 60)

# age of child. If b19_01 is not available in the data use v008 - b3_01
if ("TRUE" %in% (!("b19_01" %in% names(IRdata))))
  IRdata [[paste("b19_01")]] <- NA
if ("TRUE" %in% all(is.na(IRdata $b19_01)))
{ b19_included <- 0} else { b19_included <- 1}

if (b19_included==1) {
  IRdata <- IRdata %>%
    mutate(age = b19_01)
} else {
  IRdata <- IRdata %>%
    mutate(age = v008 - b3_01)
}


# //Number of ANC visits in 4 categories that match the table in the final report
IRdata <- IRdata %>%
  mutate(rh_anc_numvs =
           case_when(
             m14_1 == 0 ~ 0 ,
             m14_1 == 1 ~ 1 ,
             m14_1  %in% c(2,3)   ~ 2 ,
             m14_1>=4 & m14_1<=90  ~ 3 ,
             m14_1>90  ~ 9 ,
             age>=period ~ 99 )) %>%
  replace_with_na(replace = list(rh_anc_numvs = c(99))) %>%
  set_value_labels(rh_anc_numvs = c(none = 0, "1" = 1, "2-3"=2, "4+"=3, "don't know/missing"=9  )) %>%
  set_variable_labels(rh_anc_numvs = "Number of ANC visits")

# //4+ ANC visits  
IRdata <- IRdata %>%
  mutate(rh_anc_4vs =
           case_when(
             rh_anc_numvs==3 ~ 1,
             rh_anc_numvs %in% c(0,1,2,9)   ~ 0 )) %>%
  set_value_labels(rh_anc_4vs = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(rh_anc_4vs = "Attended 4+ ANC visits")


raw.dat.tmp<-IRdata
  strat <- attr(raw.dat.tmp$v025,which='labels')
  names(strat) <- tolower(names(strat))
  raw.dat.tmp$v025 <- ifelse(raw.dat.tmp$v025 == strat["urban"][[1]],'urban','rural')
  raw.dat.tmp$v025 <- factor(raw.dat.tmp$v025, levels = c('urban','rural'))
  raw.dat.tmp$v024 <- factor(unlabelled(raw.dat.tmp$v024))
  

  dat.tmp<-  raw.dat.tmp %>%
   filter( age<60)%>%
   dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
             Antenatal="rh_anc_4vs"))


```

dat.tmp: 7372 obs. of  6 variables


```{r}
table(dat.tmp$Antenatal)

```


length(unique(dat.tmp$cluster))=545
length(unique(points@data$DHSCLUST))=545, 10 mis+535 dhs


```{r}
mapfilename0 <- paste0(data.dir,"/2018/dhsFlat/ZMGE71FL/ZMGE71FL.shp")
geo0 <- readOGR(mapfilename0, verbose = FALSE)
points<-geo0

# detect points in the DHS GPS file with mis-specified coordinates and remove them if any
## 



wrong.points <- which(points@data$LATNUM < 0.0 & points@data$LONGNUM < 0.0)# miss clusters very close to 0

wrong.points <- which(points@data$LATNUM == 0.0000001 & points@data$LONGNUM == 0.0000001)
wrong.points <- which(points@data$LATNUM < 0.0000001 & points@data$LONGNUM < 0.0000001)
# wrong.points <- which(points@data$SOURCE=="MIS")

if(!is.null(dim(wrong.points))){message("There are wrong GPS points: (Longitude, Latitude) = (0, 0)")}

# remove wrong points in the data if any
dat.tmp <- dat.tmp[!(dat.tmp$cluster %in% points@data$DHSCLUST[wrong.points]),]
points@data$DHSCLUST[wrong.points] %in% unique(dat.tmp$cluster)

# add the column for GPS coordinate in the data
dat.tmp$LONGNUM <- dat.tmp$LATNUM <- NA
for(i in 1:dim(points)[1]){
  dat.tmp$LATNUM[dat.tmp$cluster == points@data$DHSCLUST[i]] <- points@data$LATNUM[i] # assign latitude to DHS cluster location
  dat.tmp$LONGNUM[dat.tmp$cluster == points@data$DHSCLUST[i]] <- points@data$LONGNUM[i] # assign longitude to DHS cluster location
}

# remove missing points in the data if any
miss <- which(dat.tmp$LATNUM == 0 & dat.tmp$LONGNUM == 0)
if(length(miss != 0)){
  dat.tmp <- dat.tmp[-miss,]
}

message("\n Assigned LAT & LONG")
```
 -158 rows as wrong.points/no gps/not dhs cluster?



```{r}
weight.strata.adm2.u1 <- readRDS(here(paste0(data.dir,"/UR/U1_fraction/admin2_u1_urban_weights.rds")))
weight.strata.adm2.u1_2018<-subset(weight.strata.adm2.u1, years == 2018)
```



```{r}
setwd(data.dir)
poly.path<-"shapeFiles/gadm41_ZMB_shp"
poly.adm0 <- readOGR(dsn = poly.path,encoding = "UTF-8", use_iconv = TRUE,
                     layer = as.character(poly.layer.adm0)) # load the national shape file
# use encoding to read special characters
poly.adm1 <- readOGR(dsn = poly.path,encoding = "UTF-8", use_iconv = TRUE,
                     layer = as.character(poly.layer.adm1)) # load the shape file of admin-1 regions

if(exists('poly.layer.adm2')){
  poly.adm2 <- readOGR(dsn = poly.path,encoding = "UTF-8", use_iconv = TRUE,
                       layer = as.character(poly.layer.adm2))} # load the shape file of admin-2 regions

# set coordinate reference system to be equal
if(exists("poly.adm2")){
  proj4string(poly.adm0) <- proj4string(poly.adm1)  <- proj4string(poly.adm2)
}else{
  proj4string(poly.adm0) <- proj4string(poly.adm1)
}

```

```{r}
# poly.adm1<-readRDS(file = "/Users/qianyu/Documents/bayes/space-time/binarymodel/data/poly.adm1.rds")
admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
colnames(admin1.mat) <- rownames(admin1.mat) <- paste0("admin1_", 1:dim(admin1.mat)[1])
admin1.names <- data.frame(GADM = eval(str2lang(poly.label.adm1)),
                           Internal = rownames(admin1.mat))
 # poly.adm2<-readRDS(file = "/Users/qianyu/Documents/bayes/space-time/binarymodel/data/poly.adm2.rds")
admin2.mat <- poly2nb(SpatialPolygons(poly.adm2@polygons))
admin2.mat <- nb2mat(admin2.mat, zero.policy = TRUE)
colnames(admin2.mat) <- rownames(admin2.mat) <- paste0("admin2_", 1:dim(admin2.mat)[1])
admin2.names <- data.frame(GADM = eval(str2lang(poly.label.adm2)),
                           Internal = rownames(admin2.mat))

```

zambia admin2: 115

```{r}

# assign admin regions based on coordinates and polygon files
adm1.ind <- exists("poly.adm1")
adm2.ind <- exists("poly.adm2")

  
points.frame <- as.data.frame(dat.tmp[,c("LONGNUM", "LATNUM")]) # retrieve GPS coordinates where data is sampled.
points.frame <- SpatialPoints(points.frame) # convert the GPS coordinates into "sp" object.
# if(adm2.ind){
  poly.over.adm2 <- SpatialPolygons(poly.adm2@polygons)
  proj4string(points.frame) <- proj4string(poly.over.adm2) <-
    proj4string(poly.adm2)  <-
    proj4string(poly.adm1)
  admin2.key <- over(points.frame, poly.over.adm2)
  # miss.frame.adm2 <- unique(points.frame@coords[which(is.na(admin2.key)),])
    miss.frame.adm2 <- points.frame@coords[which(is.na(admin2.key)),]

  # if(dim(miss.frame.adm2)[1] != 0){
  #   miss.poly.adm2 <- dist2Line( miss.frame.adm2, poly.over.adm2)

  # for(i in 1:dim(miss.poly.adm2)[1]){
  # long.ids <- which(points.frame@coords[,c("LONGNUM")] %in% miss.frame.adm2[1])
  # lat.ids <- which(points.frame@coords[,c("LATNUM")] %in% miss.frame.adm2[2])
  # ids <- intersect(long.ids, lat.ids)
  # admin2.key[ids] <- rep(miss.poly.adm2[i, 'ID'], length(ids))
    # }
  # }
  
  dat.tmp$admin2 <- admin2.key
  dat.tmp$admin2.char <- paste0("admin2_", admin2.key)
  dat.tmp$admin2.name <- as.character(eval(str2lang(poly.label.adm2)))[admin2.key]
# }else{
#   dat.tmp$admin2 <- dat.tmp$admin2.name <- NA
#   message("There is no Admin2 polygon to assign points to.")
# }

```




```{r}


#admin 2 maps to see which admin2s are NA

dat.tmp_tem<-  dat.tmp %>%
  group_by(admin2.name) %>%
  summarise(Antenatal = sum(Antenatal,na.rm = t))%>% 
   mutate(variables=rep("Antenatal",length(Antenatal))) 



# dat.tmp_tem<- as.data.frame(cbind(region=poly.adm2$NAME_2,Antenatal= tail(imod_0$summary.fitted.values,n=115)[,1],variables=rep("beta_bino",115)))
# dat.tmp_tem$Antenatal<-as.numeric ( dat.tmp_tem$Antenatal)

mapPlot(dat.tmp_tem,
        values = "Antenatal",
        variables= "variables",
        by.data = "admin2.name",
        geo =poly.adm2,
        by.geo = "NAME_2",is.long = TRUE)

```



```{r}
length(unique(dat.tmp$admin2.char))#[1] 112 missing Itezhi-tezhi, Chirundu, Shibuyunji

length(unique(dat.tmp$admin2.name))#[1] 112
dim(admin2.mat)[1]# 115 115
dat.tmp_tem[order(dat.tmp_tem$Antenatal, decreasing = TRUE),][1,]
#Lusaka            282 Antenatal
# 
# 
# dat.tmp<-dat.tmp[dat.tmp$admin2.char != "admin2_NA", ]
# dat.tmp<-  dat.tmp %>%
#   mutate(year=rep("2018",length(Antenatal))) 

```





```{r}
dat.tmp<-  dat.tmp %>%
  mutate(year=rep("2018",length(Antenatal))) 


# fit1<-smoothSurvey(as.data.frame(dat.tmp),
#                    responseType = c("binary", "gaussian")[1],
#                    responseVar= "Antenatal",
#                    regionVar = "admin2.char",
#                     clusterVar = "~cluster+householdID",#
#                     weightVar = "weight",
#                     strataVar = "strata",
#                    Amat =admin2.mat,
#                    CI = 0.95)

```



```{r}

try<-dat.tmp
HT<-try%>%
    group_by(admin2.char) %>%
    mutate(HT = sum(weight*Antenatal)/sum(weight)) %>%
     ungroup()%>%
    distinct( admin2.char, .keep_all = TRUE)
HT$HT

```






# admin-2 Beta-Binomial model with IID space effect



```{r}

   c.dat.tmp <- dat.tmp %>%
    group_by(cluster) %>%
    mutate(n = length(cluster)) %>%
    mutate(Antenatal = sum(Antenatal,na.rm = T)) %>%
    ungroup()%>%
    distinct( cluster, .keep_all = TRUE)

```


  


```{r}

 # poly.adm2@data:admin1 by alphabetical, admin2 not. 


nregion <- dim(poly.adm2)[1]
# add new rows corresponding to each region


geo_admin2<-data.frame(admin1.name=poly.adm2@data$NAME_1,admin2.name=poly.adm2@data$NAME_2,sID=c(1:115))
c.dat.tmp[(dim(c.dat.tmp)[1]+1):(dim(c.dat.tmp)[1]+nregion),"admin2.name"]<-geo_admin2$admin2.name

# c.dat.tmp$ID <- 1:dim(c.dat.tmp)[1]
c.dat.tmp$sID <- geo_admin2$sID[match(c.dat.tmp$admin2.name, geo_admin2[,"admin2.name"])]

pc.u = 1
pc.alpha = 0.01
formula <- Antenatal ~ 1 + f(sID, model = "iid", hyper = list(prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha))))
imod_0 <- inla(formula, 
               family="betabinomial",
               data=c.dat.tmp,
               Ntrials=n,
               control.predictor = list(compute=TRUE, link = 1))
#tail(imod_0$summary.fitted.values,n=nregion)
```


```{r iid, fig.show="hold", out.width="50%"}
dat.tmp.tem <- as.data.frame(cbind(
  region=poly.adm2$NAME_2[tail(c.dat.tmp$sID,n=nregion)],
  Antenatal= tail(imod_0$summary.fitted.values,n=nregion)[,1]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   


mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo = poly.adm2,
          by.geo = "NAME_2", 
          legend.label = "BB (iid)")
  
  
dat.tmp.tem<- as.data.frame(cbind(
        region=poly.adm2$NAME_2[tail(c.dat.tmp$sID,n=nregion)],
        Antenatal= tail(imod_0$summary.fitted.values,n=nregion)[,2]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo =poly.adm2,
          by.geo = "NAME_2",
          legend.label = "SD BB (iid)")
  
```




```{r iid aggregate to admin1, fig.show="hold", out.width="50%"}
dat.tmp.tem <- as.data.frame(cbind(
  region=poly.adm2$NAME_2[tail(c.dat.tmp$sID,n=nregion)],
  region1=poly.adm2$NAME_1[tail(c.dat.tmp$sID,n=nregion)],
  Antenatal= tail(imod_0$summary.fitted.values,n=nregion)[,1]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
  

dat.tmp.tem <- dat.tmp.tem %>%
    group_by(region1) %>%
    # mutate(n = length(cluster)) %>%
    mutate(Antenatal = mean(Antenatal,na.rm = T)) %>%
    ungroup()%>%
    distinct( region1, .keep_all = TRUE)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region1",
          geo = poly.adm1,
          by.geo = "NAME_1", 
          legend.label = "BB (iid)")
  

dat.tmp.tem<- as.data.frame(cbind(
        region=poly.adm2$NAME_2[tail(c.dat.tmp$sID,n=nregion)],
        region1=poly.adm2$NAME_1[tail(c.dat.tmp$sID,n=nregion)],
        Antenatal= tail(imod_0$summary.fitted.values,n=nregion)[,2]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)

dat.tmp.tem <- dat.tmp.tem %>%
    group_by(region1) %>%
    # mutate(n = length(cluster)) %>%
    mutate(Antenatal = mean(Antenatal,na.rm = T)) %>%
    ungroup()%>%
    distinct( region1, .keep_all = TRUE)
   

mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region1",
          geo =poly.adm1,
          by.geo = "NAME_1",
          legend.label = "SD BB (iid)")






```




# Admin-2 Beta-Binomial model with BYM2 spatial effect

```{r}

formula <- Antenatal ~ 1+ f(sID, model = "bym2", graph = admin2.mat, scale.model = TRUE, hyper = list(prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha))))
imod_1 <- inla(formula, 
               family="betabinomial",
               data=c.dat.tmp,
               Ntrials=n,
               control.predictor = list(compute=TRUE, link = 1))
```



```{r , fig.show="hold", out.width="50%"}
dat.tmp.tem <- as.data.frame(cbind(
  region=poly.adm2$NAME_2[tail(c.dat.tmp$sID,n=nregion)],
  Antenatal= tail(imod_1$summary.fitted.values,n=nregion)[,1]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   


mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo = poly.adm2,
          by.geo = "NAME_2", 
          legend.label = "BB (iid)")
  
  
dat.tmp.tem<- as.data.frame(cbind(
        region=poly.adm2$NAME_2[tail(c.dat.tmp$sID,n=nregion)],
        Antenatal= tail(imod_1$summary.fitted.values,n=nregion)[,2]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo =poly.adm2,
          by.geo = "NAME_2",
          legend.label = "SD BB (iid)")
  
```


# Admin-2 model with strata


```{r, out.width="50%"}

c.dat.tmp[(dim(c.dat.tmp)[1]-nregion+1):(dim(c.dat.tmp)[1]),"strata"]<-  "urban"
tmp <- c.dat.tmp[(dim(c.dat.tmp)[1]-nregion+1):(dim(c.dat.tmp)[1]), ]
tmp$strata <- "rural"
c.dat.tmp <- rbind(c.dat.tmp, tmp)

pc.u.phi <- 0.5 
pc.alpha.phi <- 2/3 

formula <- Antenatal ~ 1 + strata + 
            f(sID, model = "bym2", graph = admin2.mat, 
              hyper = list(
                  prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha)), 
                  phi = list(prior = 'pc', param = c(pc.u.phi , pc.alpha.phi))))

imod_1_strata <- inla(formula, 
                    family="betabinomial",
                    data=c.dat.tmp,
                    Ntrials=n,
                    control.predictor = list(compute=TRUE, link = 1), 
                    control.compute = list(config = TRUE))

summary(imod_1_strata)
    
```

Urban/rural specific estimates from INLA linear combinations

```{r, out.width="100%"}
dat.tmp.tem<- data.frame( 
                  region=rep(poly.adm2$NAME_2[tail(c.dat.tmp$sID,n=nregion)], 2),
                  Antenatal=  tail(imod_1_strata$summary.fitted.values[, 1],n = 2 * nregion), 
                  strata = tail(c.dat.tmp$strata, n = 2 * nregion))
mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "strata",
          by.data = "region",
          geo =poly.adm2,
          by.geo = "NAME_2",
          is.long = TRUE, 
          legend.label = "BB stratified") 
  
```




```{r, out.width="100%"}
nsamp <- 1000
samp <- inla.posterior.sample(n = nsamp, result = imod_1_strata, intern = TRUE)

draw.u <- matrix(NA, nsamp, nregion)
draw.r <- matrix(NA, nsamp, nregion)
draw.all <- matrix(NA, nsamp, nregion)

for(i in 1:length(samp)){
  tmp <- samp[[i]]$latent
  s.effect <- tmp[paste0("sID:", 1:nregion), 1]
  intercept <- tmp["(Intercept):1", 1]
  str.effect <- tmp["stratarural:1", 1]
  draw.u[i, ] <- expit(s.effect + intercept)
  draw.r[i, ] <- expit(s.effect + intercept + str.effect)
  draw.all[i, ] <- draw.u[i, ] * weight.strata.adm2.u1_2018$urban +
                   draw.r[i, ] * (1 - weight.strata.adm2.u1_2018$urban)
}

post.u <- apply(draw.u, 2, mean)
post.r <- apply(draw.r, 2, mean)
post.all <- apply(draw.all, 2, mean)


post.u.ci <- apply(draw.u, 2, quantile, probs = c(0.25,0.75))
post.r.ci <- apply(draw.r, 2,  quantile, probs = c(0.25,0.75))
post.all.ci <- apply(draw.all, 2,  quantile, probs = c(0.25,0.75))

dat.tmp.tem <- data.frame(mean = c(post.u, post.r, post.all), 
                          type = c(rep("urban", nregion), rep("rural", nregion), 
                            rep("aggregated", nregion)))
dat.tmp.tem$region <- rep(poly.adm2$NAME_2, 3)

mapPlot(dat.tmp.tem,
          values = "mean",
          variables= "type",
          by.data = "region",
          geo = poly.adm2,
          by.geo = "NAME_2",
          is.long = TRUE, 
          legend.label = "BB stratified")
  
```



```{r urban proportion}

dat.tmp.tem<- data.frame(
        region=poly.adm2$NAME_2,
        urban_prop= c(weight.strata.adm2.u1_2018$urban ))

mapPlot(dat.tmp.tem,
          variables = "urban_prop",
          by.data = "region",
          geo =poly.adm2,
          by.geo = "NAME_2",
          legend.label = "urban proportion")
```



```{r}


tb<-data.frame(
               region=poly.adm2$NAME_2, 
                # est.HT=fit1$HT$HT.est,
                # est.HT=HT$HT,
               # sd.HT=sqrt(fit1$HT$HT.var),
               # est.smth=fit1$smooth$mean,
               # sd.smth=sqrt(fit1$smooth$var),
               # lower.smth=fit1$smooth$lower,
               # upper.smth=fit1$smooth$upper,
              
               est.bb.strat=post.all,
               sd.bb.strat=apply(draw.all, 2, sd),
               lower.strat=post.all.ci[1,],
               upper.strat=post.all.ci[2,]
               
               ,
                 est.bb.bym= tail(imod_1$summary.fitted.values,n=nregion)[,1],
                sd.bb.bym=tail(imod_1$summary.fitted.values,n=nregion)[,2],
                 est.bb.iid= tail(imod_0$summary.fitted.values,n=nregion)[,1],
                sd.bb.iid=tail(imod_0$summary.fitted.values,n=nregion)[,2]
               
               
               )

 # write.csv(tb, "zambia.anc.admin2.csv")
# 
# 
tb %>%
  pivot_longer(  cols = starts_with("est"),
                 names_to = c("est"))%>%
  ggplot(data=., aes(x=region, y=value, group=est)) +
  geom_line(aes(col=est))


tb %>%
  pivot_longer(  cols = starts_with("sd"),
                 names_to = c("sd"))%>%
  ggplot(data=., aes(x=region, y=value, group=sd)) +
  geom_line(aes(col=sd))
```


```{r}
 # dat.tmp.tem<-data.frame(draw.all)

# dat.tmp.tem<-data.frame(draw.all)%>%
#   setNames(poly.adm2$NAME_1)%>%
#   group_by(region1) %>%
  


dat.tmp.tem<-as.data.frame(t(draw.all))
 dat.tmp.tem$NAME_1<- poly.adm2$NAME_1

 try1<- dat.tmp.tem%>%
 group_by(NAME_1) %>%
  summarise(across(V1:V1000, mean))

admin1.draw.all<- t(try1[,2:1001])
 
admin1.post.all <- apply(admin1.draw.all, 2, mean)
admin1.post.all.sd <- apply(admin1.draw.all, 2, sd)
admin1.post.all.ci <- apply(admin1.draw.all, 2,  quantile, probs = c(0.25,0.75))


```



#### compare admin2.strat with admin 1 results

```{r}

dt<-read_csv(file = "/Users/qianyu/Dropbox/binary_model/result/zambia.anc.admin1.csv")
dt$est.admin2.strat<-admin1.post.all
dt$sd.admin2.strat<-admin1.post.all.sd
```
```{r}

dt %>%
  pivot_longer(  cols = starts_with("est"),
                 names_to = c("est"))%>%
  ggplot(data=., aes(x=region, y=value, group=est)) +
  geom_line(aes(col=est))


dt %>%
  pivot_longer(  cols = starts_with("sd"),
                 names_to = c("sd"))%>%
  ggplot(data=., aes(x=region, y=value, group=sd)) +
  geom_line(aes(col=sd))
```


