---
title: "binary_api_womananemia"
author: "Qianyu Dong"
date: "2023-05-05"
output: html_document
---

dhs:IR dataset Individual Recode
data process code: nt_wm_any_anem 
api: AN_ANEM_W_ANY




```{r, echo=FALSE,message=FALSE, warning= FALSE}
library(dplyr)
library(rgdal)
options(warn=0)
library(spdep)
library(SUMMER)
library(geosphere)
library(stringr)
library(tidyverse)
#devtools::install_github("ropensci/rdhs")
library(rdhs)
library(Hmisc)
library(labelled)
library(INLA)
# libraries needed
# library(tidyverse)  # most variable creation here uses tidyverse 
# library(tidyselect) # used to select variables in FP_EVENTS.R
# library(haven)      # used for Haven labeled DHS variables
# library(labelled)   # used for Haven labeled variable creation
# library(expss)    # for creating tables with Haven labeled data
# library(xlsx)     # for exporting to excel
library(naniar)   # to use replace_with_na function
library(here)       # to get R project path
library(patchwork) # organize ggplot2 output nicely
#library(sjlabelled)
```




```{r}
#individual <- readRDS(here("data/DHS_data/ZMIR71DT.rds"))
country<-"Zambia"
home.dir<-"/Users/qianyu/Dropbox/binary_model"
data.dir <- paste0(home.dir,'/data/',country) # set the directory to store the data
res.dir <- paste0(home.dir,'/Results/',country) # set the directory to store the results (e.g. fitted R objects, figures, tables in .csv etc.)
info.name <- paste0(country, "_general_info.Rdata")
load(file = paste0(home.dir,'/data/Info/',info.name, sep='')) # load the country info

```

```{r}
 # setwd(here())
# children <- readRDS(here("data/DHS_data/ZMKR71DT.rds"))
# births <- readRDS(here("data/DHS_data/ZMBR71DT.rds"))
 # individual <- readRDS(here("data/DHS_data/ZMIR71DT.rds"))
 individual <- readRDS("~/Library/Caches/rdhs/datasets/ZMIR71DT.rds")
# household <- readRDS("data.dir/DHS_data/ZMHR71DT.rds")
# householdMember <- readRDS("~/Library/Caches/rdhs/datasets/ZMPR71DT.rds")

```

```{r}
IRdata <- individual %>%
  mutate(wt = v005/1000000)
# 
# *** Anemia indicators ***
# 
# //Any anemia
IRdata <- IRdata %>%
  mutate(nt_wm_any_anem =
           case_when(
             v042==1 & v457<4 ~ 1 ,
             v042==1 &  v455==0 ~ 0)) %>%
  set_value_labels(nt_wm_any_anem = c("Yes" = 1, "No"=0  )) %>%
  set_variable_labels(nt_wm_any_anem = "Any anemia - women")

```



hv025 instead of v025 in PRdata 

```{r}
raw.dat.tmp<-IRdata

  strat <- attr(raw.dat.tmp$v025,which='labels')
  names(strat) <- tolower(names(strat))
  raw.dat.tmp$hv025 <- ifelse(raw.dat.tmp$v025 == strat["urban"][[1]],'urban','rural')
  raw.dat.tmp$hv025 <- factor(raw.dat.tmp$v025, levels = c('urban','rural'))
  raw.dat.tmp$hv024 <- factor(unlabelled(raw.dat.tmp$v024))
  

   dat.tmp<-  raw.dat.tmp %>%
   # filter( age<60)%>%#for indiviudal file
     #filter( b19<=60)%>% #for birth file
    # filter( hb19<=60)%>% #for household member/PR file

   dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
             nt_wm_any_anem="nt_wm_any_anem"))
   #%>% # Antenatal="m14" for birth file
    # mutate(Antenatal = ifelse(Antenatal>3 &  Antenatal<98,1,0)) %>%
    # replace(is.na(.), 0)
    # drop_na()


 # hist(dat.tmp$Antenatal,main = "Numbers of Antenatal visits>4 in each cluster")
 
  
```




```{r}
table(dat.tmp$nt_wm_any_anem)
```



```{r}
weight.strata.adm1.u1 <- readRDS(here(paste0(res.dir,"/UR/Uf_fraction/admin1_uf_urban_weights.rds")))
weight.strata.adm1.u1_2018<-weight.strata.adm1.u1[1:10,]

```


```{r}

poly.adm1<-readRDS(paste0(data.dir,"/Geo/poly.adm1.rds"))
admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
```


# admin-1 plots

Comment: The region name matching needs to be handled in a more systematic way. But here I created the lookup table interactively
```{r}
admin1_name_table <- data.frame(by.data = sort(unique(dat.tmp$region)), by.geo = sort(poly.adm1$NAME_1))
admin1_name_table[7, 2] <- "Northern"
admin1_name_table[8, 2] <- "North-Western"
admin1_name_table$sID <- match(admin1_name_table[, 2], poly.adm1$NAME_1)
```


```{r , fig.show="hold", out.width="100%"}

par(mar = c(4, 4, .1, .1))

dat.tmp.tem <- dat.tmp %>%
      group_by(region) %>%
      summarise(Total = sum(nt_wm_any_anem > -1, na.rm = t), 
                nt_wm_any_anem = sum(nt_wm_any_anem, na.rm = t),) %>%
      mutate(Prop = nt_wm_any_anem / Total) %>% as.data.frame()

dat.tmp.tem$region <- admin1_name_table[match(dat.tmp.tem$region, admin1_name_table[,1]), 2]
   
g1 <- mapPlot(dat.tmp.tem,
          variables = "nt_wm_any_anem",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Count")
g2 <- mapPlot(dat.tmp.tem,
          variables = "Total",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Total")
g3 <- mapPlot(dat.tmp.tem,
          variables = "Prop",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Prop (unweighted)")
g1 + g2 + g3    

```



# Admin-1 direct and smoothed direct estimators

#### Direct estimates

For $y_j$ be the $j_th$ individual result and $w_j$ denote the design weight associated with this individual. Let i be area i.model

$$ \hat p^{HT}_{i}=\frac {\sum_{j \in i} y_j w_j}{\sum_{j \in i} w_j}$$

#### Smoothed direct estimates


Use direct estimate $\hat p^{HT}_{i}$ to estimate the true prevalence with random effects model,
$$log(\hat p^{HT}_{i})|\lambda_{i} \sim\textrm{Normal}(\lambda_{i}, V_{i}^{HT}),$$
$$\lambda_{i}= \mathbf x_i^{T} \mathbf{\beta} +S_i+e_i.$$
$x_i$ are areal-level covariates, $S_i$ are structured spatial trends that follow BYM model, and $e_i$ are unstructured spatial errors. Expit($p_{i}$) is the true prevalence.

```{r}
   bino.dat.tmp<-dat.tmp
   bino.dat.tmp$strata.full <- paste(bino.dat.tmp$region, bino.dat.tmp$strata)
   bino.dat.tmp$region <- admin1_name_table[match(bino.dat.tmp$region, admin1_name_table[,1]), 2]

   admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
   admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
   colnames(admin1.mat) <- rownames(admin1.mat) <-  poly.adm1$NAME_1
   clean_bino.dat.tmp<- bino.dat.tmp[complete.cases(bino.dat.tmp$nt_wm_any_anem), ]
   fit1 <- smoothSurvey(as.data.frame(clean_bino.dat.tmp),
            responseType =  "binary",
            responseVar= "nt_wm_any_anem",
            regionVar = "region",
            clusterVar = "~cluster+householdID",#+householdID same result
            weightVar = "weight",
            strataVar = "strata.full",
            Amat =admin1.mat,
            CI = 0.95)  
```

```{r}
  fit1$HT
```

```{r}
  fit1$smooth
```

```{r}
fit1$HT$HT.sd <- sqrt(fit1$HT$HT.var)
fit1$smooth$sd <- sqrt(fit1$smooth$var)
ylim1 <- range(c(fit1$HT$HT.est, fit1$smooth$mean))
ylim2 <- range(c(fit1$HT$HT.sd, fit1$smooth$sd))
```

```{r HT, fig.show="hold", out.width="100%"}
g1 <- mapPlot(fit1$HT,
          variables = "HT.est",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "HT estimator", 
          ylim = ylim1)
g2 <- mapPlot(fit1$HT,
          variables = "HT.sd",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "HT SE", 
          ylim = ylim2)

g3 <- mapPlot(fit1$smooth,
          variables = "mean",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "Smooth Direct estimator", 
          ylim = ylim1)

g4 <- mapPlot(fit1$smooth,
          variables = "sd",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "Smooth Direct SE", 
          ylim = ylim2)
(g1 + g2)/(g3 + g4)
```




```{r}
get_api_table <- function(coutry, survey, indicator, simplify = TRUE){
	call <- paste0("https://api.dhsprogram.com/rest/dhs/data?breakdown=subnational&indicatorIds=", 
			indicator, 
			"&countryIds=",
			country,
			"&surveyIds=", 
			survey, 
			"&lang=en&f=csv")
	tab <- read.csv(call)
	if(simplify){
		tab <- tab[, c("Value", "CharacteristicLabel", "ByVariableLabel")]
	}
	return(tab)
}

country <- "ZM"
survey <- "ZM2018DHS"

# Percentage of women who had a live birth in the five (or three) years preceding the survey who had 4+ antenatal care visits
# tab <- get_api_table(coutry, survey, "RH_ANCN_W_N4P")



```


```{r}
# CN_NUTS_C_HA3
# CN_NUTS_C_HA2
country <- "ZM"
survey <- "ZM2018DHS"
tab <- get_api_table(coutry, survey, "AN_ANEM_W_ANY")
tab



mapPlot(tab,
          variables = "Value",
          by.data = "CharacteristicLabel",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "API"
          )


```



```{r, fig.show="hold", out.width="50%"}

 # par(mfrow = c(1, 3))
dat.tmp.tem<-left_join( data.frame(NAME_1=tab$CharacteristicLabel,api=tab$Value),
                         data.frame(NAME_1=fit1$HT$region,dir.est=fit1$HT$HT.est),by="NAME_1")
plot(dat.tmp.tem$api/100,dat.tmp.tem$dir.est,
     xlim=round(range(dat.tmp.tem$api/100,dat.tmp.tem$dir.es),digits = 4),
     ylim=round(range(dat.tmp.tem$api/100,dat.tmp.tem$dir.es),digits = 4),
     xlab = "api", ylab = "dir.est", main = "")
abline(a = 0, b = 1, col = "red")


dat.tmp.tem<-left_join( data.frame(NAME_1=tab$CharacteristicLabel,api=tab$Value),
                         data.frame(NAME_1=fit1$smooth$region,smooth=fit1$smooth$mean),by="NAME_1")
plot(dat.tmp.tem$api/100,dat.tmp.tem$smooth,
     xlim=round(range(dat.tmp.tem$api/100,dat.tmp.tem$smooth),digits = 4),
     ylim=round(range(dat.tmp.tem$api/100,dat.tmp.tem$smooth),digits = 4),
     xlab = "api", ylab = "smooth", main = "")
abline(a = 0, b = 1, col = "red")


dat.tmp.tem<-left_join(   data.frame(NAME_1=fit1$smooth$region,smooth=fit1$smooth$mean),
                         data.frame(NAME_1=fit1$HT$region,dir.est=fit1$HT$HT.est),by="NAME_1")
plot(dat.tmp.tem$smooth,dat.tmp.tem$dir.est,
     xlim=round(range(dat.tmp.tem$smooth,dat.tmp.tem$dir.es),digits = 4),
     ylim=round(range(dat.tmp.tem$smooth,dat.tmp.tem$dir.es),digits = 4),
     xlab = "smooth", ylab = "dir.est", main = "")
abline(a = 0, b = 1, col = "red")



```








```{r}
tab[order(tab$Value),][,1:2]
fit1$HT[order(fit1$HT$HT.est),][,1:2]
fit1$smooth[order(fit1$smooth$mean),][,1:2]
```

