---
title: "binary_DPT3"
author: "Qianyu Dong"
date: "2023-04-27"
output:
  html_document: default
  pdf_document: default
---


data process code: CH_VAC
api: binary_CH_VACS_C_DP3
dhs: KR, children's

```{r, echo=FALSE,message=FALSE, warning= FALSE}
library(dplyr)
library(rgdal)
options(warn=0)
library(spdep)
library(SUMMER)
library(geosphere)
library(stringr)
library(tidyverse)
#devtools::install_github("ropensci/rdhs")
library(rdhs)
library(Hmisc)
library(labelled)
library(INLA)
# libraries needed
# library(tidyverse)  # most variable creation here uses tidyverse 
# library(tidyselect) # used to select variables in FP_EVENTS.R
# library(haven)      # used for Haven labeled DHS variables
# library(labelled)   # used for Haven labeled variable creation
# library(expss)    # for creating tables with Haven labeled data
# library(xlsx)     # for exporting to excel
library(naniar)   # to use replace_with_na function
library(here)       # to get R project path
library(patchwork) # organize ggplot2 output nicely
```




```{r}
#individual <- readRDS(here("data/DHS_data/ZMIR71DT.rds"))
country<-"Zambia"
home.dir<-"/Users/qianyu/Dropbox/binary_model"
data.dir <- paste0(home.dir,'/data/',country) # set the directory to store the data
res.dir <- paste0(home.dir,'/Results/',country) # set the directory to store the results (e.g. fitted R objects, figures, tables in .csv etc.)
info.name <- paste0(country, "_general_info.Rdata")
load(file = paste0(home.dir,'/data/Info/',info.name, sep='')) # load the country info

```

```{r}
# setwd(here())
# children <- readRDS(here("data/DHS_data/ZMKR71DT.rds"))
children <- readRDS("~/Library/Caches/rdhs/datasets/ZMKR71DT.rds")

# births <- readRDS(here("data/DHS_data/ZMBR71DT.rds"))
# individual <- readRDS(here("data/DHS_data/ZMIR71DT.rds"))
#household <- readRDS(here("data/DHS_data/ZMHR71DT.rds"))
```



```{r}
# weight variable 
KRdata <- children %>%
  mutate(wt = v005/1000000)

# age of child. If b19 is not available in the data use v008 - b3
if ("TRUE" %in% (!("b19" %in% names(KRdata))))
  KRdata [[paste("b19")]] <- NA
if ("TRUE" %in% all(is.na(KRdata$b19)))
{ b19_included <- 0} else { b19_included <- 1}

if (b19_included==1) {
  KRdata <- KRdata %>%
    mutate(age = b19)
} else {
  KRdata <- KRdata %>%
    mutate(age = v008 - b3)
}
  
# *** Two age groups used for reporting. 
KRdata <- KRdata %>%
  mutate(agegroup = 
           case_when(
             age>=12 & age<=23 ~ 1,
             age>=24 & age<=35 ~ 2  )) %>%
  set_value_labels(agegroup = c("12-23" = 1, "24-35"=2)) %>%
  set_variable_labels(agegroup = "age group of child for vaccination")

# Selecting children
# Create subset of KRfile to select for children for VAC indicators
# Select agegroup 1 or agegroup 2
KRvac <- KRdata %>%
  subset(agegroup==1 & b5==1) # select age group and live children 
  
# *******************************************************************************

# Source of vaccination information. We need this variable to code vaccination indicators by source.
KRvac <- KRvac %>%
  mutate(source = 
           case_when(h1==1 ~ 1, h1==0 | h1==2 | h1==3 ~ 2  )) %>%
  set_value_labels(source = c("card" = 1, "mother"=2)) %>%
  set_variable_labels(source = "source of vaccination information")

# *** BCG ***
# //BCG either source
KRvac <- KRvac %>%
  mutate(ch_bcg_either = 
           case_when(h2%in%c(1,2,3) ~ 1, h2%in%c(0,8)   ~ 0  )) %>%
  set_value_labels(ch_bcg_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_bcg_either = "BCG vaccination according to either source")

# //BCG mother's report
KRvac <- KRvac %>%
  mutate(ch_bcg_moth = 
           case_when(h2%in%c(1,2,3) & source==2 ~ 1, TRUE ~ 0)) %>%
  set_value_labels(ch_bcg_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_bcg_moth = "BCG vaccination according to mother")

# //BCG by card
KRvac <- KRvac %>%
  mutate(ch_bcg_card = 
           case_when(h2%in%c(1,2,3) & source==1 ~ 1, TRUE ~ 0)) %>%
  set_value_labels(ch_bcg_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_bcg_card = "BCG vaccination according to card")
 
# *** Pentavalent ***
# //DPT 1, 2, 3 either source
KRvac <- KRvac %>%
  mutate(dpt1 = case_when(h3%in%c(1,2,3) ~ 1, h3%in%c(0,8) ~ 0  )) %>%
  mutate(dpt2 = case_when(h5%in%c(1,2,3) ~ 1, h5%in%c(0,8) ~ 0  )) %>%
  mutate(dpt3 = case_when(h7%in%c(1,2,3) ~ 1, h7%in%c(0,8) ~ 0  )) %>%
  mutate(dptsum = dpt1 + dpt2 + dpt3)
# This step is performed for multi-dose vaccines to take care of any gaps in the vaccination history. 
# See DHS guide to statistics for further explanation
KRvac <- KRvac %>%
  mutate(ch_pent1_either = case_when(dptsum >=1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent1_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent1_either = "Pentavalent 1st dose vaccination according to either source") %>%
  mutate(ch_pent2_either = case_when(dptsum >=2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent2_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent2_either = "Pentavalent 2nd dose vaccination according to either source") %>%
  mutate(ch_pent3_either = case_when(dptsum >=3 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent3_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent3_either = "Pentavalent 3rd dose vaccination according to either source") 

# //DPT 1, 2, 3 mother's report
KRvac <- KRvac %>%
  mutate(ch_pent1_moth = case_when(dptsum >=1 & source==2~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent1_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent1_moth = "Pentavalent 1st dose vaccination according to mother") %>%
  mutate(ch_pent2_moth = case_when(dptsum >=2 & source==2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent2_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent2_moth = "Pentavalent 2nd dose vaccination according to mother") %>%
  mutate(ch_pent3_moth = case_when(dptsum >=3 & source==2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent3_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent3_moth = "Pentavalent 3rd dose vaccination according to mother") 

# //DPT 1, 2, 3 by card
KRvac <- KRvac %>%
  mutate(ch_pent1_card = case_when(dptsum >=1 & source==1~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent1_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent1_card = "Pentavalent 1st dose vaccination according to card") %>%
  mutate(ch_pent2_card = case_when(dptsum >=2 & source==1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent2_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent2_card = "Pentavalent 2nd dose vaccination according to card") %>%
  mutate(ch_pent3_card = case_when(dptsum >=3 & source==1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pent3_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pent3_card = "Pentavalent 3rd dose vaccination according to card") 

# *** Polio ***
# //polio 0, 1, 2, 3 either source
KRvac <- KRvac %>%
  mutate(polio1 = case_when(h4%in%c(1,2,3) ~ 1, h4%in%c(0,8) ~ 0  )) %>%
  mutate(polio2 = case_when(h6%in%c(1,2,3) ~ 1, h6%in%c(0,8) ~ 0  )) %>%
  mutate(polio3 = case_when(h8%in%c(1,2,3) ~ 1, h8%in%c(0,8) ~ 0  )) %>%
  mutate(poliosum=polio1 + polio2 + polio3)
# This step is performed for multi-dose vaccines to take care of any gaps in the vaccination history. 
# See DHS guide to statistics for further explanation
KRvac <- KRvac %>%
  mutate(ch_polio0_either = case_when(h0%in%c(1,2,3) ~ 1, h0%in%c(0,8) ~ 0 )) %>%
  set_value_labels(ch_polio0_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio0_either = "Polio at birth vaccination according to either source") %>%
  mutate(ch_polio1_either = case_when(poliosum >=1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio1_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio1_either = "Polio 1st dose vaccination according to either source") %>%
  mutate(ch_polio2_either = case_when(poliosum >=2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio2_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio2_either = "Polio 2nd dose vaccination according to either source") %>%
  mutate(ch_polio3_either = case_when(poliosum >=3 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio3_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio3_either = "Polio 3rd dose vaccination according to either source") 
 
# //polio 0, 1, 2, 3 mother's report
KRvac <- KRvac %>%
  mutate(ch_polio0_moth = case_when(h0%in%c(1,2,3) & source==2 ~ 1, TRUE ~ 0 )) %>%
  set_value_labels(ch_polio0_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio0_moth = "Polio at birth vaccination according to mother") %>%
  mutate(ch_polio1_moth = case_when(poliosum >=1 & source==2~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio1_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio1_moth = "Polio 1st dose vaccination according to mother") %>%
  mutate(ch_polio2_moth = case_when(poliosum >=2 & source==2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio2_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio2_moth = "Polio 2nd dose vaccination according to mother") %>%
  mutate(ch_polio3_moth = case_when(poliosum >=3 & source==2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio3_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio3_moth = "Polio 3rd dose vaccination according to mother") 

# //polio 0, 1, 2, 3 by card
KRvac <- KRvac %>%
  mutate(ch_polio0_card = case_when(h0%in%c(1,2,3) & source==1 ~ 1, TRUE ~ 0 )) %>%
  set_value_labels(ch_polio0_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio0_card = "Polio at birth vaccination according to card") %>%
  mutate(ch_polio1_card = case_when(poliosum >=1 & source==1~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio1_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio1_card = "Polio 1st dose vaccination according to card") %>%
  mutate(ch_polio2_card = case_when(poliosum >=2 & source==1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio2_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio2_card = "Polio 2nd dose vaccination according to card") %>%
  mutate(ch_polio3_card = case_when(poliosum >=3 & source==1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_polio3_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_polio3_card = "Polio 3rd dose vaccination according to card") 

# *** Pneumococcal  ***
# //Pneumococcal 1, 2, 3 either source
# Some surveys that do not have information on this vaccine.
KRvac <- KRvac %>%
  mutate(Pneumo1 = case_when(h54%in%c(1,2,3) ~ 1, h54%in%c(0,8) ~ 0  )) %>%
  mutate(Pneumo2 = case_when(h55%in%c(1,2,3) ~ 1, h55%in%c(0,8) ~ 0  )) %>%
  mutate(Pneumo3 = case_when(h56%in%c(1,2,3) ~ 1, h56%in%c(0,8) ~ 0  )) %>%
  mutate(Pneumosum= Pneumo1+Pneumo2+Pneumo3)
# This step is performed for multi-dose vaccines to take care of any gaps in the vaccination history. 
# See DHS guide to statistics for further explanation
KRvac <- KRvac %>%
  mutate(ch_pneumo1_either = case_when(Pneumosum >=1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo1_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo1_either = "Pneumococcal 1st dose vaccination according to either source") %>%
  mutate(ch_pneumo2_either = case_when(Pneumosum >=2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo2_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo2_either = "Pneumococcal 2nd dose vaccination according to either source") %>%
  mutate(ch_pneumo3_either = case_when(Pneumosum >=3 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo3_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo3_either = "Pneumococcal 3rd dose vaccination according to either source") 

# //Pneumococcal 1, 2, 3 mother's report
KRvac <- KRvac %>%
  mutate(ch_pneumo1_moth = case_when(Pneumosum >=1 & source==2~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo1_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo1_moth = "Pneumococcal 1st dose vaccination according to mother") %>%
  mutate(ch_pneumo2_moth = case_when(Pneumosum >=2 & source==2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo2_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo2_moth = "Pneumococcal 2nd dose vaccination according to mother") %>%
  mutate(ch_pneumo3_moth = case_when(Pneumosum >=3 & source==2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo3_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo3_moth = "Pneumococcal 3rd dose vaccination according to mother") 

# //Pneumococcal 1, 2, 3 by card
KRvac <- KRvac %>%
  mutate(ch_pneumo1_card = case_when(Pneumosum >=1 & source==1~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo1_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo1_card = "Pneumococcal 1st dose vaccination according to card") %>%
  mutate(ch_pneumo2_card = case_when(Pneumosum >=2 & source==1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo2_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo2_card = "Pneumococcal 2nd dose vaccination according to card") %>%
  mutate(ch_pneumo3_card = case_when(Pneumosum >=3 & source==1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_pneumo3_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_pneumo3_card = "Pneumococcal 3rd dose vaccination according to card") 
 
# *** Rotavirus  ****
# //Rotavirus 1, 2, 3 either source
# Some surveys that do not have information on this vaccine.
KRvac <- KRvac %>%
  mutate(rotav1 = case_when(h57%in%c(1,2,3) ~ 1, h57%in%c(0,8) ~ 0  )) %>%
  mutate(rotav2 = case_when(h58%in%c(1,2,3) ~ 1, h58%in%c(0,8) ~ 0  )) %>%
  mutate(rotav3 = case_when(h59%in%c(1,2,3) ~ 1, h59%in%c(0,8) ~ 0  )) %>%
  mutate(rotavsum= rotav1+rotav2+rotav3)
# This step is performed for multi-dose vaccines to take care of any gaps in the vaccination history. 
# See DHS guide to statistics for further explanation
KRvac <- KRvac %>%
  mutate(ch_rotav1_either = case_when(rotavsum >=1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav1_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav1_either = "Rotavirus 1st dose vaccination according to either source") %>%
  mutate(ch_rotav2_either = case_when(rotavsum >=2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav2_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav2_either = "Rotavirus 2nd dose vaccination according to either source") %>%
  mutate(ch_rotav3_either = case_when(rotavsum >=3 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav3_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav3_either = "Rotavirus 3rd dose vaccination according to either source") 

# //Rotavirus 1, 2, 3 mother's report
KRvac <- KRvac %>%
  mutate(ch_rotav1_moth = case_when(rotavsum >=1 & source==2~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav1_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav1_moth = "Rotavirus 1st dose vaccination according to mother") %>%
  mutate(ch_rotav2_moth = case_when(rotavsum >=2 & source==2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav2_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav2_moth = "Rotavirus 2nd dose vaccination according to mother") %>%
  mutate(ch_rotav3_moth = case_when(rotavsum >=3 & source==2 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav3_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav3_moth = "Rotavirus 3rd dose vaccination according to mother") 

# //Rotavirus 1, 2, 3 by card
KRvac <- KRvac %>%
  mutate(ch_rotav1_card = case_when(rotavsum >=1 & source==1~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav1_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav1_card = "Rotavirus 1st dose vaccination according to card") %>%
  mutate(ch_rotav2_card = case_when(rotavsum >=2 & source==1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav2_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav2_card = "Rotavirus 2nd dose vaccination according to card") %>%
  mutate(ch_rotav3_card = case_when(rotavsum >=3 & source==1 ~ 1, TRUE ~ 0  )) %>%
  set_value_labels(ch_rotav3_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_rotav3_card = "Rotavirus 3rd dose vaccination according to card") 
 
# *** Measles ***
# //Measles either source
KRvac <- KRvac %>%
  mutate(ch_meas_either = 
           case_when(h9%in%c(1,2,3) ~ 1, h9%in%c(0,8)   ~ 0  )) %>%
  set_value_labels(ch_meas_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_meas_either = "Measles vaccination according to either source")

# //Measles mother's report
KRvac <- KRvac %>%
  mutate(ch_meas_moth = 
           case_when(h9%in%c(1,2,3) & source==2 ~ 1, TRUE ~ 0)) %>%
  set_value_labels(ch_meas_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_meas_moth = "Measles vaccination according to mother")

# //Measles by card
KRvac <- KRvac %>%
  mutate(ch_meas_card = 
           case_when(h9%in%c(1,2,3) & source==1 ~ 1, TRUE ~ 0)) %>%
  set_value_labels(ch_meas_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_meas_card = "Measles vaccination according to card")

# *** All vaccinations ***
KRvac <- KRvac %>%
  mutate(ch_allvac_either = 
           case_when(ch_bcg_either==1&ch_pent3_either==1&ch_polio3_either==1&ch_meas_either==1 ~ 1, TRUE ~ 0)) %>%
  set_value_labels(ch_allvac_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_allvac_either = "All basic vaccinations according to either source")

KRvac <- KRvac %>%
  mutate(ch_allvac_moth = 
           case_when(ch_bcg_either==1&ch_pent3_either==1&ch_polio3_either==1&ch_meas_either==1 & source==2 ~ 1, TRUE ~ 0)) %>%
  set_value_labels(ch_allvac_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_allvac_moth = "All basic vaccinations according to mother")

KRvac <- KRvac %>%
  mutate(ch_allvac_card = 
           case_when(ch_bcg_either==1&ch_pent3_either==1&ch_polio3_either==1&ch_meas_either==1 & source==1 ~ 1, TRUE ~ 0)) %>%
  set_value_labels(ch_allvac_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_allvac_card = "All basic vaccinations according to card")

# *** No vaccinations ***
KRvac <- KRvac %>%
  mutate(ch_novac_either = 
           case_when(ch_bcg_either==0&ch_pent1_either==0&ch_pent2_either==0&ch_pent3_either==0& 
                     ch_polio0_either==0&ch_polio1_either==0&ch_polio2_either==0&ch_polio3_either==0&
                     ch_meas_either==0 ~ 1, 
                     TRUE ~ 0)) %>%
  set_value_labels(ch_novac_either = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_novac_either = "No vaccinations according to either source")

KRvac <- KRvac %>%
  mutate(ch_novac_moth = 
           case_when(ch_bcg_either==0&ch_pent1_either==0&ch_pent2_either==0&ch_pent3_either==0& 
                       ch_polio0_either==0&ch_polio1_either==0&ch_polio2_either==0&ch_polio3_either==0&
                       ch_meas_either==0& source==2 ~ 1, 
                       TRUE ~ 0)) %>%  
  set_value_labels(ch_novac_moth = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_novac_moth = "No vaccinations according to mother")

KRvac <- KRvac %>%
  mutate(ch_novac_card = 
           case_when(ch_bcg_either==0&ch_pent1_either==0&ch_pent2_either==0&ch_pent3_either==0& 
                       ch_polio0_either==0&ch_polio1_either==0&ch_polio2_either==0&ch_polio3_either==0&
                       ch_meas_either==0& source==1 ~ 1, 
                       TRUE ~ 0)) %>% 
  set_value_labels(ch_novac_card = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_novac_card = "No vaccinations according to card")
# 
# *** vaccination card possession ***
KRvac <- KRvac %>%
  mutate(ch_card_ever_had = 
           case_when(h1%in%c(1,2,3) ~ 1, TRUE  ~ 0  )) %>%
  set_value_labels(ch_card_ever_had = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_card_ever_had = "Ever had a vaccination card")

KRvac <- KRvac %>%
  mutate(ch_card_seen = 
           case_when(h1==1 ~ 1, TRUE  ~ 0  )) %>%
  set_value_labels(ch_card_seen = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(ch_card_seen = "Vaccination card seen")
```



```{r}
raw.dat.tmp<-KRvac
  strat <- attr(raw.dat.tmp$v025,which='labels')
  names(strat) <- tolower(names(strat))
  raw.dat.tmp$v025 <- ifelse(raw.dat.tmp$v025 == strat["urban"][[1]],'urban','rural')
  raw.dat.tmp$v025 <- factor(raw.dat.tmp$v025, levels = c('urban','rural'))
  raw.dat.tmp$v024 <- factor(unlabelled(raw.dat.tmp$v024))
  
#using rh_anc_4vs from dhs code
   dat.tmp<-  raw.dat.tmp %>%
  dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
             DPT3="ch_pent3_either"))

  
```

```{r}
table(dat.tmp$DPT3)
```




```{r}

poly.adm1<-readRDS(paste0(data.dir,"/Geo/poly.adm1.rds"))

 # poly.adm1<-readRDS(here("data/Geo/poly.adm1.rds"))
admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
```


# admin-1 plots

Comment: The region name matching needs to be handled in a more systematic way. But here I created the lookup table interactively
```{r}
admin1_name_table <- data.frame(by.data = sort(unique(dat.tmp$region)), by.geo = sort(poly.adm1$NAME_1))
admin1_name_table[7, 2] <- "Northern"
admin1_name_table[8, 2] <- "North-Western"
admin1_name_table$sID <- match(admin1_name_table[, 2], poly.adm1$NAME_1)
```


```{r , fig.show="hold", out.width="100%"}

par(mar = c(4, 4, .1, .1))

dat.tmp.tem <- dat.tmp %>%
      group_by(region) %>%
      summarise(Total = sum(DPT3 > -1, na.rm = t), 
                DPT3 = sum(DPT3, na.rm = t),) %>%
      mutate(Prop = DPT3 / Total) %>% as.data.frame()

dat.tmp.tem$region <- admin1_name_table[match(dat.tmp.tem$region, admin1_name_table[,1]), 2]
   
g1 <- mapPlot(dat.tmp.tem,
          variables = "DPT3",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Count")
g2 <- mapPlot(dat.tmp.tem,
          variables = "Total",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Total")
g3 <- mapPlot(dat.tmp.tem,
          variables = "Prop",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Prop (unweighted)")
g1 + g2 + g3    

```



# Admin-1 direct and smoothed direct estimators

#### Direct estimates

For $y_j$ be the $j_th$ individual result and $w_j$ denote the design weight associated with this individual. Let i be area i.model

$$ \hat p^{HT}_{i}=\frac {\sum_{j \in i} y_j w_j}{\sum_{j \in i} w_j}$$

#### Smoothed direct estimates


Use direct estimate $\hat p^{HT}_{i}$ to estimate the true prevalence with random effects model,
$$log(\hat p^{HT}_{i})|\lambda_{i} \sim\textrm{Normal}(\lambda_{i}, V_{i}^{HT}),$$
$$\lambda_{i}= \mathbf x_i^{T} \mathbf{\beta} +S_i+e_i.$$
$x_i$ are areal-level covariates, $S_i$ are structured spatial trends that follow BYM model, and $e_i$ are unstructured spatial errors. Expit($p_{i}$) is the true prevalence.

```{r}
   bino.dat.tmp<-dat.tmp
   bino.dat.tmp$strata.full <- paste(bino.dat.tmp$region, bino.dat.tmp$strata)
   bino.dat.tmp$region <- admin1_name_table[match(bino.dat.tmp$region, admin1_name_table[,1]), 2]

   admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
   admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
   colnames(admin1.mat) <- rownames(admin1.mat) <-  poly.adm1$NAME_1
   
   fit1 <- smoothSurvey(as.data.frame(bino.dat.tmp),
            responseType =  "binary",
            responseVar= "DPT3",
            regionVar = "region",
            clusterVar = "~cluster+householdID",#+householdID same result
            weightVar = "weight",
            strataVar = "strata.full",
            Amat =admin1.mat,
            CI = 0.95)  
```

```{r}
  fit1$HT
```

```{r}
  fit1$smooth
```

```{r}
fit1$HT$HT.sd <- sqrt(fit1$HT$HT.var)
fit1$smooth$sd <- sqrt(fit1$smooth$var)
ylim1 <- range(c(fit1$HT$HT.est, fit1$smooth$mean))
ylim2 <- range(c(fit1$HT$HT.sd, fit1$smooth$sd))
```

```{r HT, fig.show="hold", out.width="100%"}
g1 <- mapPlot(fit1$HT,
          variables = "HT.est",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "HT estimator", 
          ylim = ylim1)
g2 <- mapPlot(fit1$HT,
          variables = "HT.sd",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "HT SE", 
          ylim = ylim2)

g3 <- mapPlot(fit1$smooth,
          variables = "mean",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "Smooth Direct estimator", 
          ylim = ylim1)

g4 <- mapPlot(fit1$smooth,
          variables = "sd",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "Smooth Direct SE", 
          ylim = ylim2)
(g1 + g2)/(g3 + g4)
```




```{r}
get_api_table <- function(coutry, survey, indicator, simplify = TRUE){
	call <- paste0("https://api.dhsprogram.com/rest/dhs/data?breakdown=subnational&indicatorIds=", 
			indicator, 
			"&countryIds=",
			country,
			"&surveyIds=", 
			survey, 
			"&lang=en&f=csv")
	tab <- read.csv(call)
	if(simplify){
		tab <- tab[, c("Value", "CharacteristicLabel", "ByVariableLabel")]
	}
	return(tab)
}

country <- "ZM"
survey <- "ZM2018DHS"

# Percentage of women who had a live birth in the five (or three) years preceding the survey who had 4+ antenatal care visits
# tab <- get_api_table(coutry, survey, "RH_ANCN_W_N4P")



```


```{r}
# CN_NUTS_C_HA3
# CN_NUTS_C_HA2
country <- "ZM"
survey <- "ZM2018DHS"
# tab <- get_api_table(coutry, survey, "CH_VACS_C_DP3")
# tab



# mapPlot(tab,
#           variables = "Value",
#           by.data = "CharacteristicLabel",
#           geo = poly.adm1,
#           by.geo = "NAME_1",
#           legend.label = "API"
#           )
# 



```




```{r, fig.show="hold", out.width="50%"}

dat.tmp.tem<-left_join(   data.frame(NAME_1=fit1$smooth$region,smooth=fit1$smooth$mean),
                         data.frame(NAME_1=fit1$HT$region,dir.est=fit1$HT$HT.est),by="NAME_1")
plot(dat.tmp.tem$smooth,dat.tmp.tem$dir.est,
     xlim=round(range(dat.tmp.tem$smooth,dat.tmp.tem$dir.es),digits = 4),
     ylim=round(range(dat.tmp.tem$smooth,dat.tmp.tem$dir.es),digits = 4),
     xlab = "smooth", ylab = "dir.est", main = "")
abline(a = 0, b = 1, col = "red")



```








```{r}
fit1$HT[order(fit1$HT$HT.est),][,1:2]
fit1$smooth[order(fit1$smooth$mean),][,1:2]
```




