---
title: "binary_model_admin1"
author: "Qianyu Dong"
date: "2023-02-22"
output: html_document
---


```{r, echo=FALSE,message=FALSE, warning= FALSE}
library(dplyr)
library(rgdal)
options(warn=0)
library(spdep)
library(SUMMER)
library(geosphere)
library(stringr)
library(tidyverse)
#devtools::install_github("ropensci/rdhs")
library(rdhs)
library(Hmisc)
library(labelled)
library(INLA)
# libraries needed
# library(tidyverse)  # most variable creation here uses tidyverse 
# library(tidyselect) # used to select variables in FP_EVENTS.R
# library(haven)      # used for Haven labeled DHS variables
# library(labelled)   # used for Haven labeled variable creation
# library(expss)    # for creating tables with Haven labeled data
# library(xlsx)     # for exporting to excel
library(naniar)   # to use replace_with_na function
library(here)       # to get R project path
library(patchwork) # organize ggplot2 output nicely
```


```{r}
setwd(here())
children <- readRDS(here("data/DHS_data/ZMKR71DT.rds"))
births <- readRDS(here("data/DHS_data/ZMBR71DT.rds"))
individual <- readRDS(here("data/DHS_data/ZMIR71DT.rds"))
household <- readRDS(here("data/DHS_data/ZMHR71DT.rds"))
```



```{r,RH_ANC.R }

IRdata <- individual %>%
  mutate(wt = v005/1000000)

# period and age of child
# choose reference period, last 2 years (24 months) or last 5 years (60 months)
# Using a period of the last 2 years will not match final report but would provide more recent information.
# period = 24
IRdata <- IRdata %>%
  mutate(period = 60)

# age of child. If b19_01 is not available in the data use v008 - b3_01
if ("TRUE" %in% (!("b19_01" %in% names(IRdata))))
  IRdata [[paste("b19_01")]] <- NA
if ("TRUE" %in% all(is.na(IRdata $b19_01)))
{ b19_included <- 0} else { b19_included <- 1}

if (b19_included==1) {
  IRdata <- IRdata %>%
    mutate(age = b19_01)
} else {
  IRdata <- IRdata %>%
    mutate(age = v008 - b3_01)
}


# //Number of ANC visits in 4 categories that match the table in the final report
IRdata <- IRdata %>%
  mutate(rh_anc_numvs =
           case_when(
             m14_1 == 0 ~ 0 ,
             m14_1 == 1 ~ 1 ,
             m14_1  %in% c(2,3)   ~ 2 ,
             m14_1>=4 & m14_1<=90  ~ 3 ,
             m14_1>90  ~ 9 ,
             age>=period ~ 99 )) %>%
  replace_with_na(replace = list(rh_anc_numvs = c(99))) %>%
  set_value_labels(rh_anc_numvs = c(none = 0, "1" = 1, "2-3"=2, "4+"=3, "don't know/missing"=9  )) %>%
  set_variable_labels(rh_anc_numvs = "Number of ANC visits")

# //4+ ANC visits  
IRdata <- IRdata %>%
  mutate(rh_anc_4vs =
           case_when(
             rh_anc_numvs==3 ~ 1,
             rh_anc_numvs %in% c(0,1,2,9)   ~ 0 )) %>%
  set_value_labels(rh_anc_4vs = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(rh_anc_4vs = "Attended 4+ ANC visits")


```

Comment: the following reproduces the same as DHS code it seems? Then we should use the DHS codes and then modify `IRdata` object accordingly below (so that for future adaptation to other indicators we could just replace the top chunk.)

```{r}
raw.dat.tmp<-individual

  strat <- attr(raw.dat.tmp$v025,which='labels')
  names(strat) <- tolower(names(strat))
  raw.dat.tmp$v025 <- ifelse(raw.dat.tmp$v025 == strat["urban"][[1]],'urban','rural')
  raw.dat.tmp$v025 <- factor(raw.dat.tmp$v025, levels = c('urban','rural'))
  raw.dat.tmp$v024 <- factor(unlabelled(raw.dat.tmp$v024))
  
#using rh_anc_4vs from dhs code
  #  dat.tmp<-  raw.dat.tmp %>%
  # dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
  #            Antenatal="rh_anc_4vs")) %>%
  #      replace(is.na(.), 0)

   

   dat.tmp<-  raw.dat.tmp %>%
    filter( b19_01<=60)%>%#for indiviudal file
     #filter( b19<=60)%>% #for birth file
  dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
             Antenatal="m14_1")) %>% # Antenatal="m14" for birth file
    mutate(Antenatal = ifelse(Antenatal>3 &  Antenatal<98,1,0)) %>%
    # replace(is.na(.), 0)
    drop_na()


 # hist(dat.tmp$Antenatal,main = "Numbers of Antenatal visits>4 in each cluster")
 
  
```

```{r}
table(dat.tmp$Antenatal)
```


```{r}
weight.strata.adm1.u1 <- readRDS(here("data/UR/U1_fraction/admin1_u1_urban_weights.rds"))
weight.strata.adm1.u1_2018<-subset(weight.strata.adm1.u1, years == 2018)
```


```{r}
poly.adm1<-readRDS(here("data/Geo/poly.adm1.rds"))
admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
```


# admin-1 plots

Comment: The region name matching needs to be handled in a more systematic way. But here I created the lookup table interactively
```{r}
admin1_name_table <- data.frame(by.data = sort(unique(dat.tmp$region)), by.geo = sort(poly.adm1$NAME_1))
admin1_name_table[7, 2] <- "Northern"
admin1_name_table[8, 2] <- "North-Western"
admin1_name_table$sID <- match(admin1_name_table[, 2], poly.adm1$NAME_1)
```

```{r , fig.show="hold", out.width="100%"}

par(mar = c(4, 4, .1, .1))

dat.tmp.tem <- dat.tmp %>%
      group_by(region) %>%
      summarise(Total = sum(Antenatal > -1, na.rm = t), 
                Antenatal = sum(Antenatal, na.rm = t),) %>%
      mutate(Prop = Antenatal / Total) %>% as.data.frame()

dat.tmp.tem$region <- admin1_name_table[match(dat.tmp.tem$region, admin1_name_table[,1]), 2]
   
g1 <- mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Count")
g2 <- mapPlot(dat.tmp.tem,
          variables = "Total",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Total")
g3 <- mapPlot(dat.tmp.tem,
          variables = "Prop",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          is.long = FALSE, 
          legend.label = "Prop (unweighted)")
g1 + g2 + g3    

```



# Admin-1 direct and smoothed direct estimators

Comment: copy down the model specifications here.

Comment: in `smoothSurvey()`, the strata variable is the actual survey stratification variable, which is usually Admin1 crossed with U/R, instead of only the within-area stratification variable (U/R only).

Comment: I make the names consistent in both the data and the polygon files to avoid changing the labels multiple times later.

```{r}
   bino.dat.tmp<-dat.tmp
   bino.dat.tmp$strata.full <- paste(bino.dat.tmp$region, bino.dat.tmp$strata)
   bino.dat.tmp$region <- admin1_name_table[match(bino.dat.tmp$region, admin1_name_table[,1]), 2]

   admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
   admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
   colnames(admin1.mat) <- rownames(admin1.mat) <-  poly.adm1$NAME_1
   
   fit1 <- smoothSurvey(as.data.frame(bino.dat.tmp),
            responseType =  "binary",
            responseVar= "Antenatal",
            regionVar = "region",
            clusterVar = "~cluster+householdID",#+householdID same result
            weightVar = "weight",
            strataVar = "strata.full",
            Amat =admin1.mat,
            CI = 0.95)  
```

```{r}
  fit1$HT
```

```{r}
  fit1$smooth
```

```{r}
fit1$HT$HT.sd <- sqrt(fit1$HT$HT.var)
fit1$smooth$sd <- sqrt(fit1$smooth$var)
ylim1 <- range(c(fit1$HT$HT.est, fit1$smooth$mean))
ylim2 <- range(c(fit1$HT$HT.sd, fit1$smooth$sd))
```

```{r HT, fig.show="hold", out.width="100%"}
g1 <- mapPlot(fit1$HT,
          variables = "HT.est",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "HT estimator", 
          ylim = ylim1)
g2 <- mapPlot(fit1$HT,
          variables = "HT.sd",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "HT SE", 
          ylim = ylim2)

g3 <- mapPlot(fit1$smooth,
          variables = "mean",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "Smooth Direct estimator", 
          ylim = ylim1)

g4 <- mapPlot(fit1$smooth,
          variables = "sd",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1",
          legend.label = "Smooth Direct SE", 
          ylim = ylim2)
(g1 + g2)/(g3 + g4)
```





# admin-1 Beta-Binomial model with IID space effect

Comment: copy down the model specifications here.

Comment: `c.dat.tmp.birth` object name is probably too long and not clear what it is...

```{r}

   c.dat.tmp.birth <- dat.tmp %>%
    group_by(cluster) %>%
    mutate(n = length(cluster)) %>%
    mutate(Antenatal = sum(Antenatal,na.rm = T)) %>%
    ungroup()%>%
    distinct( cluster, .keep_all = TRUE)
```


Comment: I matched on the lookup table to make sure sID correspond to the same order as in the adjacency matrix.

Comment: updated prior to be PC prior.

```{r}
nregion <- dim(admin1_name_table)[1]
# add new rows corresponding to each region
c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]+1):(dim(c.dat.tmp.birth)[1]+nregion),"region"] <- admin1_name_table[,1]

c.dat.tmp.birth$ID <- 1:dim(c.dat.tmp.birth)[1]
c.dat.tmp.birth$sID <- admin1_name_table$sID[match(c.dat.tmp.birth$region, admin1_name_table[,1])]

pc.u = 1
pc.alpha = 0.01
formula <- Antenatal ~ 1 + f(sID, model = "iid", hyper = list(prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha))))
imod_0 <- inla(formula, 
               family="betabinomial",
               data=c.dat.tmp.birth,
               Ntrials=n,
               control.predictor = list(compute=TRUE, link = 1))
tail(imod_0$summary.fitted.values,n=nregion)

```


```{r iid, fig.show="hold", out.width="50%"}
dat.tmp.tem <- as.data.frame(cbind(
  region=poly.adm1$NAME_1,
  Antenatal= tail(imod_0$summary.fitted.values,n=nregion)[,1]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1", 
          legend.label = "BB (iid)")
  
  
dat.tmp.tem<- as.data.frame(cbind(
        region=poly.adm1$NAME_1,
        Antenatal= tail(imod_0$summary.fitted.values,n=nregion)[,2]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",
          legend.label = "SD BB (iid)")
  
```




# Admin-1 Beta-Binomial model with BYM2 spatial effect


Comment: I use the same dataset as before to avoid copy pasting errors.

```{r}
formula <- Antenatal ~ 1+ f(sID, model = "bym2", graph = admin1.mat, scale.model = TRUE, hyper = list(prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha))))
imod_1 <- inla(formula, 
               family="betabinomial",
               data=c.dat.tmp.birth,
               Ntrials=n,
               control.predictor = list(compute=TRUE, link = 1))
```


```{r bym, fig.show="hold", out.width="50%"}
dat.tmp.tem<- as.data.frame(cbind(
                  region=poly.adm1$NAME_1,
                  Antenatal= tail(imod_1$summary.fitted.values,n=nregion)[,1]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo = poly.adm1,
          by.geo = "NAME_1", 
          legend.label = "BB (BYM2)")
  
  
dat.tmp.tem<- as.data.frame(cbind(
        region=poly.adm1$NAME_1,
        Antenatal= tail(imod_1$summary.fitted.values,n=nregion)[,2]))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
mapPlot(dat.tmp.tem,
          variables = "Antenatal",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",
          legend.label = "SD BB (BYM2)")
```



# admin-1 model with strata

Comment: copy down the model specifications here maybe?

Comment: I also removed repeated data generating steps and built from previous data frame.

```{r}

c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]-nregion+1):(dim(c.dat.tmp.birth)[1]),"strata"]<-  "urban"
tmp <- c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]-nregion+1):(dim(c.dat.tmp.birth)[1]), ]
tmp$strata <- "rural"
c.dat.tmp.birth <- rbind(c.dat.tmp.birth, tmp)

pc.u.phi <- 0.5 
pc.alpha.phi <- 2/3 

formula <- Antenatal ~ 1 + strata + 
            f(sID, model = "bym2", graph = admin1.mat, 
              hyper = list(
                  prec = list(prior = "pc.prec", param = c(pc.u , pc.alpha)), 
                  phi = list(prior = 'pc', param = c(pc.u.phi , pc.alpha.phi))))

imod_1_strata <- inla(formula, 
                    family="betabinomial",
                    data=c.dat.tmp.birth,
                    Ntrials=n,
                    control.predictor = list(compute=TRUE, link = 1))

summary(imod_1_strata)
    
# p_urban =rep(imod_1_strata$summary.fixed[1,1],545)+ bym+ imod$summary.random$ID[,2]

```

```{r}
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,
                                  Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[1:10,1]*weight.strata.adm1.u1_2018$urban
+tail(imod_1_strata$summary.fitted.values,n=20)[11:20,1]*weight.strata.adm1.u1_2018$rural

,variables=rep("strata",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
```







```{r strata, fig.show="hold", out.width="50%"}
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[1:10,1],variables=rep("urban",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[1:10,2],variables=rep("var",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
  
  dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[11:20,1],variables=rep("rural",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[11:20,2],variables=rep("var",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
```































<!-- 


---
title: "binary_model_admin1"
author: "Qianyu Dong"
date: "2023-02-22"
output: html_document
---
```{r, echo=FALSE,message=FALSE, warning= FALSE}



library(dplyr)
library(rgdal)
options(warn=0)
library(spdep)
library(SUMMER)
library(geosphere)
library(stringr)
library(tidyverse)
#devtools::install_github("ropensci/rdhs")
library(rdhs)
library(Hmisc)
library(labelled)
library(INLA)

# libraries needed
# library(tidyverse)  # most variable creation here uses tidyverse 
# library(tidyselect) # used to select variables in FP_EVENTS.R
# library(haven)      # used for Haven labeled DHS variables
# library(labelled)   # used for Haven labeled variable creation
# library(expss)    # for creating tables with Haven labeled data
# library(xlsx)     # for exporting to excel
library(naniar)   # to use replace_with_na function
# library(here)       # to get R project path



```


```{r}
children <- readRDS("~/Library/Caches/rdhs/datasets/ZMKR71DT.rds")
births <- readRDS("~/Library/Caches/rdhs/datasets/ZMBR71DT.rds")
individual <- readRDS("~/Library/Caches/rdhs/datasets/ZMIR71DT.rds")
household <- readRDS("~/Library/Caches/rdhs/datasets/ZMHR71DT.rds")
```



```{r,RH_ANC.R }

IRdata <- individual %>%
  mutate(wt = v005/1000000)

# period and age of child
# choose reference period, last 2 years (24 months) or last 5 years (60 months)
# Using a period of the last 2 years will not match final report but would provide more recent information.
# period = 24
IRdata <- IRdata %>%
  mutate(period = 60)

# age of child. If b19_01 is not available in the data use v008 - b3_01
if ("TRUE" %in% (!("b19_01" %in% names(IRdata))))
  IRdata [[paste("b19_01")]] <- NA
if ("TRUE" %in% all(is.na(IRdata $b19_01)))
{ b19_included <- 0} else { b19_included <- 1}

if (b19_included==1) {
  IRdata <- IRdata %>%
    mutate(age = b19_01)
} else {
  IRdata <- IRdata %>%
    mutate(age = v008 - b3_01)
}


# //Number of ANC visits in 4 categories that match the table in the final report
IRdata <- IRdata %>%
  mutate(rh_anc_numvs =
           case_when(
             m14_1 == 0 ~ 0 ,
             m14_1 == 1 ~ 1 ,
             m14_1  %in% c(2,3)   ~ 2 ,
             m14_1>=4 & m14_1<=90  ~ 3 ,
             m14_1>90  ~ 9 ,
             age>=period ~ 99 )) %>%
  replace_with_na(replace = list(rh_anc_numvs = c(99))) %>%
  set_value_labels(rh_anc_numvs = c(none = 0, "1" = 1, "2-3"=2, "4+"=3, "don't know/missing"=9  )) %>%
  set_variable_labels(rh_anc_numvs = "Number of ANC visits")

# //4+ ANC visits  
IRdata <- IRdata %>%
  mutate(rh_anc_4vs =
           case_when(
             rh_anc_numvs==3 ~ 1,
             rh_anc_numvs %in% c(0,1,2,9)   ~ 0 )) %>%
  set_value_labels(rh_anc_4vs = c("Yes" = 1, "No"=0)) %>%
  set_variable_labels(rh_anc_4vs = "Attended 4+ ANC visits")


```




```{r}
births <- readRDS("~/Library/Caches/rdhs/datasets/ZMBR71DT.rds")
raw.dat.tmp<-individual

  strat <- attr(raw.dat.tmp$v025,which='labels')
  names(strat) <- tolower(names(strat))
  raw.dat.tmp$v025 <- ifelse(raw.dat.tmp$v025 == strat["urban"][[1]],'urban','rural')
  raw.dat.tmp$v025 <- factor(raw.dat.tmp$v025, levels = c('urban','rural'))
  raw.dat.tmp$v024 <- factor(unlabelled(raw.dat.tmp$v024))
  
#using rh_anc_4vs from dhs code
  #  dat.tmp<-  raw.dat.tmp %>%
  # dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
  #            Antenatal="rh_anc_4vs")) %>%
  #      replace(is.na(.), 0)

   

   dat.tmp<-  raw.dat.tmp %>%
    filter( b19_01<=60)%>%#for indiviudal file
     #filter( b19<=60)%>% #for birth file
  dplyr::  select(c(cluster="v001", householdID= "v002",region="v024", weight="v005", strata="v025",
             Antenatal="m14_1")) %>% # Antenatal="m14" for birth file
    mutate(Antenatal = ifelse(Antenatal>3 &  Antenatal<98,1,0)) %>%
    # replace(is.na(.), 0)
    drop_na()


 # hist(dat.tmp$Antenatal,main = "Numbers of Antenatal visits>4 in each cluster")
 
  
```

```{r}
table(dat.tmp$m14_1)
table(dat.tmp$Antenatal)
```


```{r}

country <- 'Zambia'
home.dir<-"/Users/qianyu/Documents/bayes/space-time/UN-Subnational-Estimates-main_old"
res.dir <- paste0(home.dir,'/Results/',country) 
setwd(paste0(res.dir,'/UR'))
weight.strata.adm1.u1 <- readRDS(paste0('U1_fraction/','admin1_u1_urban_weights.rds'))
weight.strata.adm1.u1_2018<-weight.strata.adm1.u1[181:190,]
```


```{r}
poly.adm1<-readRDS(file = "/Users/qianyu/Documents/bayes/space-time/binarymodel/data/poly.adm1.rds")
admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)

```


# admin-1 plots

```{r , fig.show="hold", out.width="50%"}

par(mar = c(4, 4, .1, .1))

  dat.tmp.tem<-  dat.tmp %>%
      group_by(region) %>%
      summarise(Antenatal = sum(Antenatal,na.rm = t))

 poly.adm1<-readRDS(file = "/Users/qianyu/Documents/bayes/space-time/binarymodel/data/poly.adm1.rds")
 dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal=dat.tmp.tem$Antenatal,variables=rep("Antenatal",10)))
 dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
  dat.tmp.tem<-  dat.tmp %>%
      group_by(region) %>%
      summarise(n = n())
  
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,n=dat.tmp.tem$n,variables=rep("n",10)))
 dat.tmp.tem$n<-as.numeric ( dat.tmp.tem$n)
   
  mapPlot(dat.tmp.tem,
          values = "n",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  

```



# admin-1 direct&smoothed_direct



```{r}

   bino.dat.tmp<-dat.tmp

   admin1.mat <- poly2nb(SpatialPolygons(poly.adm1@polygons))
   admin1.mat <- nb2mat(admin1.mat, zero.policy = TRUE)
   colnames(admin1.mat) <- rownames(admin1.mat) <-  levels(as.factor(dat.tmp$region))
   # bino.dat.tmp<- bino.dat.tmp%>% drop_na()
   
   
   fit1<-smoothSurvey(as.data.frame(bino.dat.tmp),
            responseType = c("binary", "gaussian")[1],
            responseVar= "Antenatal",
            regionVar = "region",
            clusterVar = "~cluster+householdID",#+householdID same result
            weightVar = "weight",
            strataVar = "strata",
            Amat =admin1.mat,
            CI = 0.95)

   
```

```{r}
  fit1$HT
```
```{r HT, fig.show="hold", out.width="50%"}
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal_HT= fit1$HT[,2],variables=rep("direct",10)))
dat.tmp.tem$Antenatal_HT<-as.numeric ( dat.tmp.tem$Antenatal_HT)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal_HT",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
  dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal_HT= fit1$HT[,3],variables=rep("var",10)))
dat.tmp.tem$Antenatal_HT<-as.numeric ( dat.tmp.tem$Antenatal_HT)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal_HT",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
```



```{r}
  fit1$smooth
```


```{r smooth, fig.show="hold", out.width="50%"}
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal_HT= fit1$smooth[,2],variables=rep("smooth",10)))
dat.tmp.tem$Antenatal_HT<-as.numeric ( dat.tmp.tem$Antenatal_HT)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal_HT",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
  dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal_HT= fit1$smooth[,3],variables=rep("var",10)))
dat.tmp.tem$Antenatal_HT<-as.numeric ( dat.tmp.tem$Antenatal_HT)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal_HT",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
```





# admin-1 model 

```{r}

   dat.tmp<- dat.tmp %>%
    group_by(cluster) %>%
    mutate(Antenatal = sum(Antenatal,na.rm = t)) %>%
    mutate(n = length(cluster)) %>%
     ungroup()%>%
    distinct( cluster, .keep_all = TRUE)
```


```{r}
c.dat.tmp.birth<-dat.tmp
c.dat.tmp.birth$ID<-1:dim(c.dat.tmp.birth)[1]
c.dat.tmp.birth$sID<-as.numeric(c.dat.tmp.birth$region)
 # to save results  
# c.dat.tmp.birth<-c.dat.tmp.birth%>%add_row(head(c.dat.tmp.birth,10))
# c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]-9):dim(c.dat.tmp.birth)[1],2]<-rep(unique(c.dat.tmp.birth$region),1)
# c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]-9):dim(c.dat.tmp.birth)[1],8]<- c(1:10)
# c.dat.tmp.birth[546:555,c(1,2:7)]<-NA

c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]+1):(dim(c.dat.tmp.birth)[1]+10),"region"]<-rep(unique(c.dat.tmp.birth$region),1)
c.dat.tmp.birth$sID<-as.numeric(c.dat.tmp.birth$region)


formula <- Antenatal ~ 1+ f(sID, model = "iid")
imod_0 <- inla(formula, family="betabinomial",data=c.dat.tmp.birth,Ntrials=n,control.predictor = list(compute=TRUE))
tail(imod_0$summary.fitted.values,n=10)

```


```{r iid, fig.show="hold", out.width="50%"}
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_0$summary.fitted.values,n=10)[,1],variables=rep("beta_bino",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_0$summary.fitted.values,n=10)[,2],variables=rep("var",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
```




# admin-1 model with bym



```{r}
c.dat.tmp.birth<-dat.tmp
c.dat.tmp.birth$ID<-1:dim(c.dat.tmp.birth)[1]
c.dat.tmp.birth$sID<-as.numeric(c.dat.tmp.birth$region)
 # to save results  
# c.dat.tmp.birth<-c.dat.tmp.birth%>%add_row(head(c.dat.tmp.birth,10))
# c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]-9):dim(c.dat.tmp.birth)[1],2]<-rep(unique(c.dat.tmp.birth$region),1)
# c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]-9):dim(c.dat.tmp.birth)[1],8]<- c(1:10)
# c.dat.tmp.birth[546:555,c(1,2:7)]<-NA

c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]+1):(dim(c.dat.tmp.birth)[1]+10),"region"]<-rep(unique(c.dat.tmp.birth$region),1)
c.dat.tmp.birth$sID<-as.numeric(c.dat.tmp.birth$region)

formula <- Antenatal ~ 1+ f(sID, model = "bym2", graph = admin1.mat)
imod_1 <- inla(formula, family="betabinomial",data=c.dat.tmp.birth,Ntrials=n,control.predictor = list(compute=TRUE))
# tail(imod_1$summary.fitted.values)

```


```{r bym, fig.show="hold", out.width="50%"}
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1$summary.fitted.values,n=10)[,1],variables=rep("beta_bino",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_0$summary.fitted.values,n=10)[,2],variables=rep("beta_bino",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
```



# admin-1 model with strata

```{r}


c.dat.tmp.birth<-dat.tmp
c.dat.tmp.birth$ID<-1:dim(c.dat.tmp.birth)[1]
c.dat.tmp.birth$sID<-as.numeric(c.dat.tmp.birth$region)
c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]+1):(dim(c.dat.tmp.birth)[1]+20),"region"]<-rep(unique(c.dat.tmp.birth$region),2)
c.dat.tmp.birth$sID<-as.numeric(c.dat.tmp.birth$region)
c.dat.tmp.birth[(dim(c.dat.tmp.birth)[1]-19):(dim(c.dat.tmp.birth)[1]),"strata"]<-  c(rep("urban",10),rep("rural",10))

formula <- Antenatal ~ 1+strata+ f(sID, model = "bym2", graph = admin1.mat)
imod_1_strata <- inla(formula, family="betabinomial",data=c.dat.tmp.birth,Ntrials=n)

tail(imod_1_strata$summary.fitted.values,n=20)[1:10,1]*weight.strata.adm1.u1_2018$urban
+tail(imod_1_strata$summary.fitted.values,n=20)[11:20,1]*weight.strata.adm1.u1_2018$rural

  
  
# p_urban =rep(imod_1_strata$summary.fixed[1,1],545)+ bym+ imod$summary.random$ID[,2]

```

```{r}
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,
                                  Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[1:10,1]*weight.strata.adm1.u1_2018$urban
+tail(imod_1_strata$summary.fitted.values,n=20)[11:20,1]*weight.strata.adm1.u1_2018$rural

,variables=rep("strata",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
```







```{r strata, fig.show="hold", out.width="50%"}
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[1:10,1],variables=rep("urban",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[1:10,2],variables=rep("var",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
  
  dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[11:20,1],variables=rep("rural",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
  
dat.tmp.tem<- as.data.frame(cbind(region=poly.adm1$NAME_1,Antenatal= tail(imod_1_strata$summary.fitted.values,n=20)[11:20,2],variables=rep("var",10)))
dat.tmp.tem$Antenatal<-as.numeric ( dat.tmp.tem$Antenatal)
   
  mapPlot(dat.tmp.tem,
          values = "Antenatal",
          variables= "variables",
          by.data = "region",
          geo =poly.adm1,
          by.geo = "NAME_1",is.long = TRUE)
  
```



 -->






























